---
title: "Support for non-state armed groups as domestic signaling to opposition groups"
output:
  html_document:
    df_print: paged
  pdf_document: default
editor_options:
  chunk_output_type: console
---

This work includes data for all nondemocracies, defined as a Regimes of the World with ambiguous cases (v2x_regime_amb) < 4, Electoral autocracies and below. 

## Data Load

```{r echo=FALSE}
options(scipen = 999)
library(stargazer)
library(here)

autocracies_data <- read.csv(here("data","autocracies_data_v.csv"))

autocracies_data$NAGs_Supported <- autocracies_data$NumNAG_S
autocracies_data$NAGS_with_Training_Camps <- autocracies_data$Num_S_TrainCamp
autocracies_data$opposition_size <- autocracies_data$oppsize_norm
autocracies_data$W <- autocracies_data$W_norm
autocracies_data$distance_between_capitals <- autocracies_data$capdist


hurdle_count_n <- autocracies_data[which(autocracies_data$NumNAG_S > 0),]

hurdle_count_t <- autocracies_data[which(autocracies_data$Num_S_TrainCamp >0),]

autocracies_data$at_least_1_NAG_supported <- ifelse(autocracies_data$NAGs_Supported > 0,1,0)

autocracies_data$at_least_1_Training_Camp <- ifelse(autocracies_data$NAGS_with_Training_Camps>0,1,0)

autocracies_data$Training_Camp_and_Democratic_Target <- ifelse((autocracies_data$NAGS_with_Training_Camps>0 & autocracies_data$targ_democratic == 1),1,0)



```

at_least_1_NAG_supported
at_least_1_Training_Camp
Training_Camp_and_Democratic_Target


```{r echo=FALSE, comment = ""}

#normalized measure of W based on Smith and Bueno de Mesquita 2022
summary(autocracies_data$W)

#normalized measure of opposition size
summary(autocracies_data$opposition_size)


#Number of NAGS with training camps hosted in supporting country
summary(autocracies_data$NAGS_with_Training_Camps)

#Number of NAGS actively supported
summary(autocracies_data$NAGs_Supported)


# ratio of opposition size measure to W measure (both normalized)
# 
cat("ratio of opposition size measure to W measure (both normalized)")
summary(autocracies_data$opp_W_ratio)

# ratio of support group size measure to W measure (both normalized)
summary(autocracies_data$supp_W_ratio)

# ratio of opposition group size measure to support group size measure to W measure (both normalized)
summary(autocracies_data$opp_supp_ratio)

# supporter is democratic (binary)
summary(autocracies_data$supp_democratic)

#target is democratic (binary)
summary(autocracies_data$targ_democratic)

```

## Summary Plots

```{r echo=FALSE}

hist(autocracies_data$NAGs_Supported, main = "Histogram of Number of groups \n actively supported \n autocracies only")

hist(autocracies_data$NAGS_with_Training_Camps, main = "Histogram of Number of groups \n supported with training camps \n autocracies only")

hist(autocracies_data$at_least_1_NAG_supported, main = "Histogram of \n at least one NAG supported \n autocracies only")

hist(autocracies_data$at_least_1_Training_Camp, main = "Histogram of \n at least one Training Camp hosted \n autocracies only")

hist(autocracies_data$Training_Camp_and_Democratic_Target, main = "Histogram of \n at least one Training Camp hosted \n for group with democratic target \n autocracies only")






hist(autocracies_data$opposition_size, main = "Histogram of \n Opposition Size")

hist(autocracies_data$W, main = "Histogram of \n Minimal Winning Coalition Size (W)")



```

Models:

- HW: Autocratic regimes which have smaller winning coalitions (W)  and are also more reliant on ideological support groups will be more likely to support NAGS, all else equal. (Smaller W predicts greater use of private payoffs to maintain W. I argue that ideological payoffs substitute for private payoffs.)




```{r echo=FALSE}
library(MASS)
library(pscl)
library(VGAM)


formulaw1 <- NAGs_Supported ~ W *  v2exl_legitideol + WarOnTerror + ColdWar + distance_between_capitals  

formulaw1b <- NAGS_with_Training_Camps ~ W * v2exl_legitideol +  WarOnTerror + ColdWar + distance_between_capitals  


# quasipoisson model using number of groups supported

w1_numSq <- glm(formula = formulaw1, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(w1_numSq)
exp(coef(w1_numSq))


# Hurdle model

w1_hurdle <- hurdle(formula = formulaw1, data = autocracies_data)
summary(w1_hurdle)

w1_hurdle_part <- glm(at_least_1_NAG_supported ~ W * v2exl_legitideol +  WarOnTerror + ColdWar + distance_between_capitals , family  = binomial(link = "logit"), data = autocracies_data)
summary(w1_hurdle_part)
exp(coef(w1_hurdle_part))



w1_count_part <- vglm(formula = formulaw1, family  = pospoisson(), data = hurdle_count_n)
summary(w1_count_part)



#Model using number of groups with training camps in country
#

# quasipoisson model using number of groups supported

w1_numSqb <- glm(formula = formulaw1b, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(w1_numSqb)
exp(coef(w1_numSqb))


# Hurdle model

w1_hurdleb <- hurdle(formula = formulaw1b, data = autocracies_data)
summary(w1_hurdleb)

w1_hurdle_partb <- glm(at_least_1_NAG_supported ~ W * v2exl_legitideol + WarOnTerror + ColdWar + distance_between_capitals , family  = binomial(link = "logit"), data = autocracies_data)
summary(w1_hurdle_partb)
exp(coef(w1_hurdle_partb))



w1_count_part <- vglm(formula = formulaw1, family  = pospoisson(), data = hurdle_count_n)
summary(w1_count_part)

cat("\n w1_hurdle - number supported \n")

## Exponentiated coefficients
expCoefw1 <- exp(coef((w1_hurdle)))
expCoefw1 <- matrix(expCoefw1, ncol = 2)
rownames(expCoefw1) <- names(coef(w1_hurdle_part))
colnames(expCoefw1) <- c("Count_model","Zero_hurdle_model")
expCoefw1

cat("\n w1_hurdle - number with training camps \n")

## Exponentiated coefficients
expCoefw1b <- round(exp(coef((w1_hurdleb))), digits = 5)
expCoefw1b <- matrix(expCoefw1b, ncol = 2)
rownames(expCoefw1b) <- names(coef(w1_hurdle_partb))
colnames(expCoefw1b) <- c("Count_model","Zero_hurdle_model")
expCoefw1b

# library(stargazer)
# stargazer(w1_hurdle_part)
# stargazer(w1_hurdle_partb)
# 
# stargazer(w1_numSq)
# stargazer(w1_numSqb)

```


H1: Autocratic regimes with larger opposition groups will be more likely to actively support at least one NAG, all else equal.

```{r}

formulah1 <- NAGs_Supported ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals  + W


h1_hurdle_part <- glm(at_least_1_NAG_supported ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals+ W, family  = binomial(link = "logit"), data = autocracies_data)
summary(h1_hurdle_part)
exp(coef(h1_hurdle_part))




```


H2: Autocratic regimes with larger opposition groups will be more likely to actively support NAGs by hosting training camps, all else equal. 


```{r}



formulah2 <- NAGS_with_Training_Camps ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals  + W + NAGs_Supported


h2_hurdle_part <- glm(at_least_1_Training_Camp~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals  + W + NAGs_Supported, family  = binomial(link = "logit"), data = autocracies_data)
summary(h2_hurdle_part)
exp(coef(h2_hurdle_part))

h2_hurdle_partb <- glm(at_least_1_Training_Camp ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals  + W, family  = binomial(link = "logit"), data = autocracies_data)
summary(h2_hurdle_partb)
exp(coef(h2_hurdle_partb))



```


H3: Autocratic regimes with larger opposition groups will be more likely to actively support NAGS that target democracies by hosting training camps, all else equal. 


```{r}

h3_hurdle_part <- glm(Training_Camp_and_Democratic_Target ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals  + W, family  = binomial(link = "logit"), data = autocracies_data)
summary(h3_hurdle_part)
exp(coef(h3_hurdle_part))

h3_hurdle_partb <- glm(Training_Camp_and_Democratic_Target ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals  + W + at_least_1_Training_Camp, family  = binomial(link = "logit"), data = autocracies_data)
summary(h3_hurdle_partb)
exp(coef(h3_hurdle_partb))

```


H4: Autocratic regimes with larger opposition groups and pro-democracy civil society movements will be more likely to actively support NAGS that target democracies by hosting training camps, all else equal. 

```{r}
h4_hurdle_part <- glm(Training_Camp_and_Democratic_Target ~ opposition_size *  v2csanmvch_4 + WarOnTerror + ColdWar + distance_between_capitals + W, family  = binomial(link = "logit"), data = autocracies_data)
summary(h4_hurdle_part)
exp(coef(h4_hurdle_part))


h4_hurdle_partb <- glm(Training_Camp_and_Democratic_Target ~ opposition_size *  v2csanmvch_4 + WarOnTerror + ColdWar + distance_between_capitals + W + at_least_1_Training_Camp, family  = binomial(link = "logit"), data = autocracies_data)
summary(h4_hurdle_partb)
exp(coef(h4_hurdle_partb))


```

H5: Large anti-system civil society movements - v2csantimv - or pro-democracy civil society movements - v2csanmvch_4

```{r}

h5_hurdle_part <- glm(Training_Camp_and_Democratic_Target ~ v2csantimv + WarOnTerror + ColdWar + distance_between_capitals + W, family  = binomial(link = "logit"), data = autocracies_data)
summary(h5_hurdle_part)
exp(coef(h5_hurdle_part))

h5_hurdle_part <- glm(Training_Camp_and_Democratic_Target ~ v2csantimv + WarOnTerror + ColdWar + distance_between_capitals + W, family  = binomial(link = "logit"), data = autocracies_data)
summary(h5_hurdle_part)
exp(coef(h5_hurdle_part))



```

Next steps: Instrumental variable using 2S IV Regression with a linear probability model

Instrument is Civil Society Organization Women's Participation (v2csgender)

While there is a strong theoretical link between the strength of civil society and the strength of opposition groups, which makes some measure of civil society an appropriate instrument it is necessary to find an appropriate measure of civil society. There are two issues here. First, many measures of civil society include an often heavy emphasis on the sorts of non-governmental organizations that are often the target or even creation of democracy promotion efforts by the West. Thus, these measures suffer the same endogeneity problem the instrumental variable treatment approach is intended to solve. Second, many measures of civil society such as institutional rules and structures of civil society organizations are one step removed from measuring the actual strength of civil society. Without developing a separate measure of civil society strength, which would be worthwhile but well beyond the scope of this analysis, the VDem data set offers a measure which more closely ties civil society to opposition -  women's participation in civil society.

It has been asserted that women's participation in civil society anti-system movements represent a tipping point to large scale opposition, mass protest, and even outright rebellion. 

Dabiri, Arastoo. “‘Woman, Life, Freedom’: A Movement in Progress in Iran.” Dignity: A Journal of Analysis of Exploitation and Violence 8, no. 1 (2023): 5. https://doi.org/10.23860/dignity.2023.08.01.05

Ms Constitution. “‘Woman, Life, Liberty’ in Iran and the Role of Academia.” Nature Human Behaviour 7, no. 1 (January 2023): 3–5. https://doi.org/10.1038/s41562-022-01504-6

Henshaw, Alexis Leanna. “Where Women Rebel.” International Feminist Journal of Politics 18, no. 1 (January 2, 2016): 39–60. https://doi.org/10.1080/14616742.2015.1007729




```{r}

#h3as LPM

h3_lpm <- lm(Training_Camp_and_Democratic_Target ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals + W, data = autocracies_data)
summary(h3_lpm)

library(ivreg)

h3_iv <- ivreg(Training_Camp_and_Democratic_Target ~  WarOnTerror + ColdWar + distance_between_capitals + W | opposition_size | v2csgender, data = autocracies_data)

summary(h3_iv)

library("modelsummary")
m_list <- list(OLS = h3_lpm, IV = h3_iv)
msummary(m_list)

modelplot(m_list)

h1_lpm <- lm(at_least_1_NAG_supported ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals+ W, data = autocracies_data)
summary(h1_lpm)

h1_iv <- ivreg(at_least_1_NAG_supported ~ WarOnTerror + ColdWar + distance_between_capitals + W | opposition_size | v2csgender, data = autocracies_data)

summary(h1_iv)

m_list1 <- list(OLS = h1_lpm, IV = h1_iv)
msummary(m_list1)

modelplot(m_list1)


h2_lpm <- lm(at_least_1_Training_Camp ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals  + W, data = autocracies_data)
summary(h2_lpm)

h2_iv <- ivreg(at_least_1_Training_Camp ~ WarOnTerror + ColdWar + distance_between_capitals  + W | opposition_size | v2csgender, family  = binomial(link = "logit"), data = autocracies_data)
summary(h2_iv)

m_list2 <- list(OLS = h2_lpm, IV = h2_iv)
msummary(m_list2)

modelplot(m_list2)





```

Cases


```{r}

cases <- autocracies_data[which(autocracies_data$at_least_1_Training_Camp == 1 & autocracies_data$oppsize_norm > .66979),]

countercases <- autocracies_data[which(autocracies_data$at_least_1_Training_Camp == 1 & autocracies_data$oppsize_norm < .58),]
```

