---
title: "R Notebook"
output:
  html_document:
    df_print: paged
editor_options: 
  chunk_output_type: console
---

## Data Load

```{r echo=FALSE}
options(scipen = 999)
library(stargazer)
library(here)

autocracies_data <- read.csv(here("data","autocracies_data.csv"))

autocracies_data$NAGs_Supported <- autocracies_data$NumNAG_S
autocracies_data$NAGS_with_Training_Camps <- autocracies_data$Num_S_TrainCamp
autocracies_data$opposition_size <- autocracies_data$oppsize_norm
autocracies_data$W <- autocracies_data$W_norm
autocracies_data$distance_between_capitals <- autocracies_data$capdist


hurdle_count_n <- autocracies_data[which(autocracies_data$NumNAG_S > 0),]

hurdle_count_t <- autocracies_data[which(autocracies_data$Num_S_TrainCamp >0),]



```

## Summary Stats



```{r echo=FALSE, comment = ""}

#normalized measure of W based on Smith and Bueno de Mesquita 2022
summary(autocracies_data$W)

#normalized measure of opposition size
summary(autocracies_data$opposition_size)


#Number of NAGS with training camps hosted in supporting country
summary(autocracies_data$NAGS_with_Training_Camps)

#Number of NAGS actively supported
summary(autocracies_data$NAGs_Supported)


# ratio of opposition size measure to W measure (both normalized)
# 
cat("ratio of opposition size measure to W measure (both normalized)")
summary(autocracies_data$opp_W_ratio)

# ratio of support group size measure to W measure (both normalized)
summary(autocracies_data$supp_W_ratio)

# ratio of opposition group size measure to support group size measure to W measure (both normalized)
summary(autocracies_data$opp_supp_ratio)

# supporter is democratic (binary)
summary(autocracies_data$supp_democratic)

#target is democratic (binary)
summary(autocracies_data$targ_democratic)




```

## Summary Plots

```{r echo=FALSE}

hist(autocracies_data$NAGs_Supported, main = "Histogram of Number of groups \n actively supported \n autocracies only")

hist(autocracies_data$NAGS_with_Training_Camps, main = "Histogram of Number of groups \n supported with training camps \n autocracies only")

hist(autocracies_data$opposition_size, main = "Histogram of \n Opposition Size")

hist(autocracies_data$W, main = "Histogram of \n Minimal Winning Coalition Size (W)")



```

## Models

- HW: Autocratic regimes with smaller W will be more likely to support NAGS, all else equal. 

```{r echo=FALSE}
library(MASS)
library(pscl)
library(VGAM)

formulaw1 <- NAGs_Supported ~ W + WarOnTerror + ColdWar + distance_between_capitals  

formulaw1b <- NAGS_with_Training_Camps ~ W + WarOnTerror + ColdWar + distance_between_capitals  


# quasipoisson model using number of groups supported

w1_numSq <- glm(formula = formulaw1, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(w1_numSq)
exp(coef(w1_numSq))


# Hurdle model

w1_hurdle <- hurdle(formula = formulaw1, data = autocracies_data)
summary(w1_hurdle)

w1_hurdle_part <- glm(I(NAGs_Supported>0) ~ W + WarOnTerror + ColdWar + distance_between_capitals , family  = binomial(link = "logit"), data = autocracies_data)
summary(w1_hurdle_part)
exp(coef(w1_hurdle_part))



w1_count_part <- vglm(formula = formulaw1, family  = pospoisson(), data = hurdle_count_n)
summary(w1_count_part)



#Model using number of groups with training camps in country
#

# quasipoisson model using number of groups supported

w1_numSqb <- glm(formula = formulaw1b, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(w1_numSqb)
exp(coef(w1_numSqb))


# Hurdle model

w1_hurdleb <- hurdle(formula = formulaw1b, data = autocracies_data)
summary(w1_hurdleb)

w1_hurdle_partb <- glm(I(NAGS_with_Training_Camps>0) ~ W + WarOnTerror + ColdWar + distance_between_capitals , family  = binomial(link = "logit"), data = autocracies_data)
summary(w1_hurdle_partb)
exp(coef(w1_hurdle_partb))

w1_count_part <- vglm(formula = formulaw1, family  = pospoisson(), data = hurdle_count_n)
summary(w1_count_part)

cat("\n w1_hurdle - number supported \n")

## Exponentiated coefficients
expCoefw1 <- exp(coef((w1_hurdle)))
expCoefw1 <- matrix(expCoefw1, ncol = 2)
rownames(expCoefw1) <- names(coef(w1_hurdle_part))
colnames(expCoefw1) <- c("Count_model","Zero_hurdle_model")
expCoefw1

cat("\n w1_hurdle - number with training camps \n")

## Exponentiated coefficients
expCoefw1b <- round(exp(coef((w1_hurdleb))), digits = 5)
expCoefw1b <- matrix(expCoefw1b, ncol = 2)
rownames(expCoefw1b) <- names(coef(w1_hurdle_partb))
colnames(expCoefw1b) <- c("Count_model","Zero_hurdle_model")
expCoefw1b

# library(stargazer)
# stargazer(w1_hurdle_part)
# stargazer(w1_hurdle_partb)
# 
# stargazer(w1_numSq)
# stargazer(w1_numSqb)

```


- H1: Autocratic regimes with large opposition groups will be more likely to support NAGS, all else equal. 

                + H1a: Higher likelihood of supporting at least one NAG.

                + H1b: Higher number of NAGS supported.
                
```{r echo=FALSE}

formulah1 <- NAGs_Supported ~ v2csprtcpt + WarOnTerror + ColdWar + distance_between_capitals  + W


# quasipoisson model using number of groups supported

h1_q <- glm(formula = formulah1, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h1_q)
exp(coef(h1_q))


# Hurdle model

h1_hurdle <- hurdle(formula = formulah1, data = autocracies_data)
summary(h1_hurdle)

h1_hurdle_part <- glm(I(NAGs_Supported>0) ~ v2csprtcpt + WarOnTerror + ColdWar + distance_between_capitals  + W, family  = binomial(link = "logit"), data = autocracies_data)
summary(h1_hurdle_part)
exp(coef(h1_hurdle_part))

h1_count_part <- vglm(formula = formulah1, family  = pospoisson(), data = hurdle_count_n)
summary(h1_count_part)


cat("\n h1_hurdle - number supported \n")

## Exponentiated coefficients
expCoefh1 <- exp(coef((h1_hurdle)))
expCoefh1 <- matrix(expCoefh1, ncol = 2)
rownames(expCoefh1) <- names(coef(h1_hurdle_part))
colnames(expCoefh1) <- c("Count_model","Zero_hurdle_model")
expCoefh1

# library(stargazer)
# stargazer(h1_q)
# stargazer(h1_hurdle)


```


- H2: Autocratic regimes with large opposition groups will be more likely to support NAGS by hosting training camps, all else equal. 

                + H2a: Higher likelihood of supporting at least one NAG.

                + H2b: Higher number of NAGS supported.
                
```{r echo=FALSE}



#H2 - Models using number of groups with training camps in country
#

formulah2 <- NAGS_with_Training_Camps ~ v2csprtcpt + WarOnTerror + ColdWar + distance_between_capitals  + W + NAGs_Supported



# quasipoisson model using number of groups supported

h2_q <- glm(formula = formulah2, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h2_q)
exp(coef(h2_q))


# Hurdle model

h2_hurdle <- hurdle(formula = formulah2, data = autocracies_data)
summary(h2_hurdle)

h2_hurdle_part <- glm(I(NAGS_with_Training_Camps>0) ~ v2csprtcpt + WarOnTerror + ColdWar + distance_between_capitals  + W + NAGs_Supported, family  = binomial(link = "logit"), data = autocracies_data)
summary(h2_hurdle_part)
exp(coef(h2_hurdle_part))

h2_count_part <- vglm(formula = formulah2, family  = pospoisson(), data = hurdle_count_t)
summary(h2_count_part)



cat("\n h2_hurdle - number with training camps \n")



## Exponentiated coefficients
expCoefh2 <- round(exp(coef((h2_hurdle))), digits = 5)
expCoefh2 <- matrix(expCoefh2, ncol = 2)
rownames(expCoefh2) <- names(coef(h2_hurdle_part))
colnames(expCoefh2) <- c("Count_model","Zero_hurdle_model")
expCoefh2


# stargazer(h2_hurdle)

# stargazer(h2_q)
# 

```


- H3: Autocratic regimes with large opposition groups will be more likely to support NAGS that target democracies.\\

                + H3a: Higher likelihood of supporting at least one NAG that targets a democracy.

                + H3b: Number of NAGs that target a democracy supported will be higher. 
                
```{r echo=FALSE}

formulah3 <- NAGs_Supported ~ targ_democratic * v2csprtcpt + WarOnTerror + ColdWar + distance_between_capitals  + W

# quasipoisson model using number of groups supported

h3_q <- glm(formula = formulah3, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h3_q)
exp(coef(h3_q))

# Hurdle model

h3_hurdle <- hurdle(formula = formulah3, data = autocracies_data)
summary(h3_hurdle)

h3_hurdle_part <- glm(I(NAGs_Supported>0) ~ targ_democratic * v2csprtcpt + WarOnTerror + ColdWar + distance_between_capitals  + W, family  = binomial(link = "logit"), data = autocracies_data)
summary(h3_hurdle_part)
exp(coef(h3_hurdle_part))

h3_count_part <- vglm(formula = formulah3, family  = pospoisson(), data = hurdle_count_n)
summary(h3_count_part)


## Exponentiated coefficients
expCoefh3 <- exp(coef((h3_hurdle)))
expCoefh3 <- matrix(expCoefh3, ncol = 2)
rownames(expCoefh3) <- names(coef(h3_hurdle_part))
colnames(expCoefh3) <- c("Count_model","Zero_hurdle_model")
expCoefh3

# stargazer(h3_hurdle)
# stargazer(h3_q)


```



- H4: Autocratic regimes with large opposition groups and democratizing civil society groups  will be more likely to support NAGS that target democracies by hosting training camps, all else equal. 

                + H4a: Higher likelihood of supporting at least one NAG targeting democracies by hosting training camps.

                + H4b: Number of NAGs supported by hosting training camps will be higher. 

```{r echo=FALSE}

# v2csantimv CSO anti-system movement
# 
#  CSO anti-system movement character (C) (v2csanmvch) - 4 is democratic

formulah4 <- NAGS_with_Training_Camps ~ targ_democratic * v2csanmvch_4  + WarOnTerror + ColdWar + distance_between_capitals  + W + NAGs_Supported

# quasipoisson model using number of groups supported

h4_q <- glm(formula = formulah4, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h4_q)
exp(coef(h4_q))

# Hurdle model

h4_hurdle <- hurdle(formula = formulah4, data = autocracies_data)
summary(h4_hurdle)

h4_hurdle_part <- glm(I(NAGS_with_Training_Camps>0) ~ targ_democratic + v2csanmvch_4 + WarOnTerror + ColdWar + distance_between_capitals  + W + NAGs_Supported, family  = binomial(link = "logit"), data = autocracies_data)
summary(h4_hurdle_part)
exp(coef(h4_hurdle_part))


h4_count_part <- vglm(formula = formulah4, family  = pospoisson(), data = hurdle_count_t)
summary(h4_count_part)


cat("\n h2_hurdle - number with training camps \n")

## Exponentiated coefficients
expCoefh4 <- round(exp(coef((h4_hurdle))), digits = 5)
expCoefh4 <- matrix(expCoefh4, ncol = 2)
rownames(expCoefh4) <- names(coef(h4_hurdle_part))
colnames(expCoefh4) <- c("Count_model","Zero_hurdle_model")
expCoefh4

# stargazer(h4_q)
# stargazer(h4_hurdle)




```

```{r}

        
h5_hurdle_part <- glm(I(NAGS_with_Training_Camps>0 & targ_democratic == 1) ~ opposition_size + v2csanmvch_4 + WarOnTerror + ColdWar + distance_between_capitals  + W + NAGs_Supported, family  = binomial(link = "logit"), data = autocracies_data)
summary(h5_hurdle_part)
exp(coef(h5_hurdle_part))

h5_hurdle_partb <- glm(I(NAGS_with_Training_Camps>0 & targ_democratic == 1) ~ opposition_size * v2csanmvch_4 + WarOnTerror + ColdWar + distance_between_capitals  + W + NAGs_Supported, family  = binomial(link = "logit"), data = autocracies_data)
summary(h5_hurdle_partb)
exp(coef(h5_hurdle_partb))


```



## Tables

```{r echo=FALSE}

stargazer(h1_q,h1_hurdle_part, type = "text")
expCoefh1

stargazer(h2_q,h2_hurdle_part, type = "text")
expCoefh2

stargazer(h3_q,h3_hurdle_part, type = "text")
expCoefh3

stargazer(h4_q,h4_hurdle_part, type = "text")
expCoefh4
```


## Model plots

```{r echo=FALSE}

clog <- function(x) log(x + 0.5)

cfac <- function(x, breaks = NULL) {
+ if(is.null(breaks)) breaks <- unique(quantile(x, 0:10/10))
+ x <- cut(x, breaks, include.lowest = TRUE, right = FALSE)
+ levels(x) <- paste(breaks[-length(breaks)], ifelse(diff(breaks) > 1,
+ c(paste("-", breaks[-c(1, length(breaks))] - 1, sep = ""), "+"), "")) + return(x)}



```


```{r echo=FALSE}


library(ggplot2)

ggplot(autocracies_data, aes(opposition_size,NAGs_Supported)) +
        geom_count() +
        geom_smooth()

ggplot(autocracies_data, aes(opposition_size,NAGS_with_Training_Camps)) +
        geom_count() +
        geom_smooth()

library(sjPlot)
library(sjlabelled)
library(sjmisc)
theme_set(theme_sjplot())



plot_model(h1_q, title = "H1: Count of groups supported")

plot_model(h1_hurdle_part, title = "H1: Hurdle model \n Likelihood of greater than 1 group supported")



plot_model(h2_q, title = "H2: Count of groups with training camps hosted")

plot_model(h2_hurdle_part, title = "H2: Hurdle model \n Likelihood of greater than 1 group with training camp hosted")



plot_model(h3_q, title = "H3: Count of groups supported")

plot_model(h3_hurdle_part, title = "H3: Hurdle model \n Likelihood of greater than 1 group supported")



plot_model(h4_q, title = "H4: Count of groups with training camps hosted")

plot_model(h4_hurdle_part, title = "H4: Hurdle model \n Likelihood of greater than 1 group with training camp hosted")




plot_model(h1_count_part, title = "H1: Hurdle model \n Truncated Poisson Count Above Hurdle")
plot_model(h2_count_part, title = "H2: Hurdle model \n Truncated Poisson Count Above Hurdle")
plot_model(h3_count_part, title = "H3: Hurdle model \n Truncated Poisson Count Above Hurdle")
plot_model(h4_count_part, title = "H4: Hurdle model \n Truncated Poisson Count Above Hurdle")

```

```{r}




```


## Tables for LaTeX

```{r echo=FALSE}
# 
# stargazer(h1_q,h1_hurdle_part)
# expCoefh1
# 
# stargazer(h2_q,h2_hurdle_part)
# expCoefh2
# 
# stargazer(h3_q,h3_hurdle_part)
# expCoefh3
# 
# stargazer(h4_q,h4_hurdle_part)
# expCoefh4
# 
# stargazer(h1_q,h2_q,h3_q,h4_q)
# 
# stargazer(h1_hurdle_part,h2_hurdle_part,h3_hurdle_part,h4_hurdle_part)
# 

```

##IV regression

### Stage I - Two Stage IV Regression

```{r}

stage_1a <- lm(opposition_size ~ v2csprtcpt, data = autocracies_data)
summary(stage_1a)

stage_1b  <- lm(opposition_size ~ v2cseeorgs, data = autocracies_data)
summary(stage_1b)

stage_1c <- lm(opposition_size ~ v2x_cspart, data = autocracies_data)
summary(stage_1c)

stage_1d <- lm(opposition_size ~ v2csantimv, data = autocracies_data)
summary(stage_1d)

stage_1e <- lm(opposition_size ~ v2csstruc_3, data = autocracies_data)
summary(stage_1e)



# do regressions for partial F-tests
# first-stage:
fs = lm(I(NAGS_with_Training_Camps>0 & targ_democratic == 1) ~ opposition_size + v2csprtcpt, data = autocracies_data)
# null first-stage (i.e. exclude IVs):
fn = lm(I(NAGS_with_Training_Camps>0 & targ_democratic == 1) ~ opposition_size, data = autocracies_data)

anova(fs,fn)

# simple F-test
library(AER)
waldtest(fs, fn)$F[2]
# F-test robust to heteroskedasticity
waldtest(fs, fn, vcov = vcovHC(fs, type="HC0"))$F[2]







```

### Two stage residual inclusion

```{r}
library(OneSampleMR)

tsrilogitfit <- tsri(I(NAGS_with_Training_Camps>0) ~ opposition_size | v2x_cspart, data = autocracies_data, link = "logit")
summary(tsrilogitfit)




```



## Democracy attacks - autocracy promotion

use v2csanmvch

```{r}

# 3.10.0.8  CSO anti-system movement character (C) (v2csanmvch)Project Manager(s): Michael BernhardAdditional versions: *_nrQuestion: How would you characterize the anti-system movement(s) identified in the previousquestion?Clarification: Check all that apply.Responses:0: Works through legal channels, for the most part. (0=No, 1=Yes) [v2csanmvch_0]1: Participates in elections. (0=No, 1=Yes) [v2csanmvch_1]2: Works through a mix of legal and extra-legal channels. (0=No, 1=Yes) [v2csanmvch_2]3: Insurrectionary. (0=No, 1=Yes) [v2csanmvch_3]4: Democratic. Perceived by most disinterested observers as willing to play by the rules ofthe democratic game, willing to respect constitutional provisions or electoral outcomes, andwilling to relinquish power (under democratic auspices). (0=No, 1=Yes) [v2csanmvch_4]5: Anti-democratic.  Perceived by most disinterested observers as unwilling to play by therules of the democratic game, not willing to respect constitutional provisions or electoraloutcomes, and/or not willing to relinquish power (under democratic auspices).  (0=No,1=Yes) [v2csanmvch_5]6: Leftist, socialist, communist. (0=No, 1=Yes) [v2csanmvch_6]7: Rightist, conservative, party of order. (0=No, 1=Yes) [v2csanmvch_7]8: Ethnolinguistic, tribe, kinship, clan. (0=No, 1=Yes) [v2csanmvch_8]9: Separatist or autonomist. (0=No, 1=Yes) [v2csanmvch_9]10: Religious. (0=No, 1=Yes) [v2csanmvch_10]11: Paramilitary. (0=No, 1=Yes) [v2csanmvch_11]12: Heavily engaged in criminal activity,e.g., narcotics, bootlegging, illegal exploitation ofnatural resources, extortion, kidnapping. (0=No, 1=Yes) [v2csanmvch_12]

```

```{r}

c <- length(autocracies_data$e_legparty)

n <- sum(is.na(autocracies_data$e_legparty))

answer <- n/c

answer

```



## Additional checks