---
title: "R Notebook"
output:
  html_document:
    df_print: paged
editor_options: 
  chunk_output_type: console
---

```{r echo = FALSE}

options(scipen=999)

#Loading NAGS dyadic (supporter-target) data

library(here)
library(readr)
nags_data1 <- read_delim(here("data","Dyadic_Target-Supporter_active_support.csv"), delim = ";", escape_double = FALSE, trim_ws = TRUE)


nags_data1 <- nags_data1[which(nags_data1$Year > 1945),]

nags_data1$year <- nags_data1$Year
nags_data1$COWcode <- nags_data1$SupNum_COW

head(nags_data1)

```

```{r echo=FALSE}

# creating polity scores for supporter and target countries

#load polity data set for suppoters
#
library(readxl)
support_polity <- read_excel("data/p5v2018.xls")
head(support_polity)

#create score labels for supporters
support_polity$supporter_p5 <- support_polity$p5
support_polity$supporter_cyear <- support_polity$cyear
support_polity$supporter_flag <- support_polity$flag
support_polity$SupNum_COW <- support_polity$ccode 
support_polity$supporter_democ <- support_polity$democ 
support_polity$supporter_autoc <- support_polity$autoc
support_polity$supporter_polity <- support_polity$polity
support_polity$supporter_polity2 <- support_polity$polity2
support_polity$supporter_durable <- support_polity$durable

#select only the supporter named variables

support_polity <- support_polity[c(6,38:46)]

#repeat the above for target countries

#load polity data set for targets
#
target_polity <- read_excel("data/p5v2018.xls")
head(target_polity)

#create score labels for targets
target_polity$target_p5 <- target_polity$p5
target_polity$target_cyear <- target_polity$cyear
target_polity$target_flag <- target_polity$flag
target_polity$TarNum_COW <- target_polity$ccode 
target_polity$target_democ <- target_polity$democ 
target_polity$target_autoc <- target_polity$autoc
target_polity$target_polity <- target_polity$polity
target_polity$target_polity2 <- target_polity$polity2
target_polity$target_durable <- target_polity$durable

#select only the target named variables

target_polity <- target_polity[c(6,38:46)]


```

```{r echo=FALSE}
# Merge polity data for supporters
library(dplyr)
nags_data1 <- left_join(nags_data1,support_polity, by = c("SupNum_COW","year"))

# Merge polity data for targets

nags_data1 <- left_join(nags_data1,target_polity, by = c("TarNum_COW","year"))

# add national capabilities data for supporters and targets

# load national material capabilities data
# 

NMC<- read_csv(here("data","NMC-60-abridged.csv"))
head(NMC)

NMC$COWcode <- NMC$ccode

NMC <- NMC[which(NMC$year > 1945 & NMC$year < 2011),]

NMC <- NMC[c(3:12)]

NMC_supp <- NMC

NMC_supp$SupNum_COW <- NMC_supp$COWcode
NMC_supp$supporter_milex <- NMC_supp$milex
NMC_supp$supporter_milper <- NMC_supp$milper
NMC_supp$supporter_irst <- NMC_supp$irst
NMC_supp$supporter_pec <- NMC_supp$pec
NMC_supp$supporter_tpop <- NMC_supp$tpop
NMC_supp$supporter_upop <- NMC_supp$upop
NMC_supp$supporter_cinc <- NMC_supp$cinc

NMC_supp <- NMC_supp[c(1,11:18)]

NMC_targ <- NMC

NMC_targ$TarNum_COW <- NMC_targ$COWcode
NMC_targ$target_milex <- NMC_targ$milex
NMC_targ$target_milper <- NMC_targ$milper
NMC_targ$target_irst <- NMC_targ$irst
NMC_targ$target_pec <- NMC_targ$pec
NMC_targ$target_tpop <- NMC_targ$tpop
NMC_targ$target_upop <- NMC_targ$upop
NMC_targ$target_cinc <- NMC_targ$cinc

NMC_targ <- NMC_targ[c(1,11:18)]

nags_data1 <- left_join(nags_data1,NMC_supp, by = c("SupNum_COW","year"))

nags_data1 <- left_join(nags_data1,NMC_targ, by = c("TarNum_COW","year"))


```



```{r echo=FALSE}

countries_data <- read_csv(here("data","vdem_plus_w.csv"))
head(countries_data)

countries_data <- countries_data[which(countries_data$year < 2011),]

library(dplyr)

full_data <- left_join(nags_data1,countries_data, by = c("COWcode","year"))

# vdem_select1 <- vdem_w_select[which(vdem_w_select$year > 1945),]




```


## To Do (variables)

                + Use Cshapes to add minimum distance between states in dyad - done
                + Use Cshapes to add distance between capitals in dyad - done
                + Add variable for violent repression (PTS data has limitations - only post-1976 and includes all state violence not just political repression)
                + State capacity
                
## Additional Sources

                + For protests, riots, and violence against civilians)
                (https://acleddata.com/data-export-tool/
                + For general levels of poltical terror - Political Terror Scale


```{r echo=FALSE}
# summary(full_data$W_norm)

# create a democracy target variable
# 


full_data$targ_democratic <- ifelse(full_data$target_polity > 6,1,0)
# summary(full_data$targ_democratic)

#create a binary democracy variable for supporters 

full_data$supp_democratic <- ifelse(full_data$supporter_polity > 6,1,0)
# summary(full_data$supp_democratic)




# normalize opposition and support group size variables
# 


minopp <- min(full_data$v2regoppgroupssize, na.rm = TRUE)
maxopp <- max(full_data$v2regoppgroupssize, na.rm = TRUE)


full_data$oppsize_norm <- (full_data$v2regoppgroupssize - minopp ) / (maxopp - minopp)


minsupp <- min(full_data$v2regsupgroupssize, na.rm = TRUE)
maxsupp <- max(full_data$v2regsupgroupssize, na.rm = TRUE)

full_data$suppsize_norm <- (full_data$v2regsupgroupssize - minsupp) / (maxsupp - minsupp)


summary(full_data$suppsize_norm)
summary(full_data$oppsize_norm)



# create a variable of ratio of opposition to support group size

full_data$opp_supp_ratio <- full_data$oppsize_norm / full_data$suppsize_norm
# summary(full_data$opp_supp_ratio)

# create variable of ratio of support size score to W score
# 

full_data$supp_W_ratio <- full_data$suppsize_norm / full_data$W_norm
# summary(full_data$supp_W_ratio)


# create variable of ratio of opposition to W

full_data$opp_W_ratio <- full_data$oppsize_norm / full_data$W_norm
# summary(full_data$opp_W_ratio)


# create variables for Cold War and War on Terror (post-911)

full_data$ColdWar <- ifelse(full_data$year < 1991,1,0)
# summary(full_data$ColdWar)

full_data$WarOnTerror <- ifelse(full_data$year > 2001,1,0)
# summary(full_data$WarOnTerror)


## use cshapes data to include minimum distance and distance between capitals
## 

library(cshapes)

#create a vector of dates for years in data set

cap_dist <- distlist(date = as.Date("2010-01-01"), type = "capdist", useGW = FALSE)

cap_dist$SupNum_COW <- cap_dist$ccode1
cap_dist$TarNum_COW <- cap_dist$ccode2
cap_dist <- cap_dist[c(3:5)]

# min_dist <- distlist(date = as.Date("2010-01-01"), type = "mindist", useGW = FALSE)
# 
# min_dist$SupNum_COW <- min_dist$ccode1
# min_dist$TarNum_COW <- min_dist$ccode2
# min_dist <- min_dist[c(3:5)]
# 
# write.csv(min_dist, file = here("data","min_dist.csv"))
# 

min_dist <- read_csv(here("data","min_dist.csv"))
min_dist <- min_dist[c(2:4)]

full_data <- left_join(full_data,cap_dist, by = c("SupNum_COW","TarNum_COW"))

full_data <- left_join(full_data,min_dist, by = c("SupNum_COW","TarNum_COW"))


# retrieve state capacity data
# 

library(haven)
state_cap <- read_dta(here("data","StateCapacityDataset_v1.dta"))
View(state_cap)

state_cap$SupNum_COW <- state_cap$ccode
state_cap$capacity <- state_cap$Capacity

minmilexpercap <- min(state_cap$milexpercap, na.rm = TRUE)
maxmilexpercap <- max(state_cap$milexpercap, na.rm = TRUE)

state_cap$milex_percap_norm <- (state_cap$milexpercap - minmilexpercap) / (maxmilexpercap - minmilexpercap)


minmilpercap <- min(state_cap$milpercap, na.rm = TRUE)
maxmilpercap <- max(state_cap$milpercap, na.rm = TRUE)

state_cap$milpercap_norm <- (state_cap$milpercap - minmilpercap) / (maxmilpercap - minmilpercap)

state_cap <- state_cap[c(3,34:37)]

full_data <- left_join(full_data,state_cap, by = c("SupNum_COW","year"))

#create binary variable for autocracy (used later to create subsets)
full_data$supp_autocratic <- ifelse(full_data$supporter_polity < -5,1,0)




# Political Terror Scale data
# 

pts <- read.csv(here("data","PTS-2022.csv"))
head(pts)

#prepare data to merge

pts$SupNum_COW <- pts$COW_Code_N
pts$year <- pts$Year

pts <- pts[6:16]

# create a new dataframe with all other data plus pts data

pts_full_data <- left_join(full_data,pts, by = c("SupNum_COW","year"))
pts_full_data <- pts_full_data[which(pts_full_data$year >= 1976),]



# create dataframe with just non-democractic supporter states
# 

pts_autocracies <- pts_full_data[which(pts_full_data$supp_autocratic == 1),]

autocracies_data <- full_data[which(full_data$supp_autocratic == 1),]


```

## Descriptive data

### Summary Statistics


```{r echo=FALSE, comment = ""}

# ratio of opposition size measure to W measure (both normalized)
# 
cat("ratio of opposition size measure to W measure (both normalized)")
summary(full_data$opp_W_ratio)

# ratio of support group size measure to W measure (both normalized)
summary(full_data$supp_W_ratio)

# ratio of opposition group size measure to support group size measure to W measure (both normalized)
summary(full_data$opp_supp_ratio)

# supporter is democratic (binary)
summary(full_data$supp_democratic)

#target is democratic (binary)
summary(full_data$targ_democratic)

#normalized measure of W based on Smith and Bueno de Mesquita 2022
summary(full_data$W_norm)

## Autocracy binary in full data (mean is proportion)
## 
summary(full_data$supp_autocratic)

summary(autocracies_data$Num_S_TrainCamp)


```

### Plots

```{r echo=FALSE}

hist(full_data$opp_supp_ratio, main = "Histogram of \n Opposition to support ratio")

hist(full_data$Num_S_TrainCamp, main = "Histogram of Number of groups \n supported with training camps \n all regime types")

hist(autocracies_data$Num_S_TrainCamp, main = "Histogram of Number of groups \n supported with training camps \n autocracies only")


```


## Hypotheses

                + H1 Regimes with higher levels of opposition are more likely to support NAGS, all else equal
                
                + H2 Regimes with higher levels of opposition are more likely to support NAGS that target democracies, all else equal
                
                + H3 Regimes with lower levels of military capability are more likely to support NAGS, all else equal
                
                + H4 Regimes with lower levels of millitary capability are more likely to support NAGs that target democracies, all else equal
                
                + H5 Regimes with lower levels of state capacity are more likely to support NAGS, all else equal. 
                
                +H6 Regimes with lower levels of state capacity are more likely to support NAGS that target democracies, all else equal.
                
                + H7 If regimes substitute NAGS for repression, regimes with lower levels of repression are more likely to support NAGS, all else equal.
                + H8 If signals are successful, regimes with higher support for NAGS will have lower levels of protest 
        
                
## Models

### Issues

                + Zero-inflation
                + overdispersion
                
### Poisson, quasipoisson, and hurdle models for legitimating ideology               
                
```{r echo=FALSE}
library(MASS)
library(pscl)


## model on legitimation by ideology autocracies only
## 


model_ideo <- glm(NumNAG_S ~ v2exl_legitideol, family  = poisson(link = "log"), data = autocracies_data)
summary(model_ideo)
exp(coef(model_ideo))

model_ideo_qp <- glm(NumNAG_S ~ v2exl_legitideol, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(model_ideo_qp)
exp(coef(model_ideo_qp))


model_ideo_hurdle <- hurdle(NumNAG_S ~ v2exl_legitideol | v2exl_legitideol, data = autocracies_data)
summary(model_ideo_hurdle)

hurdle_part_ideo <- glm(I(NumNAG_S>0) ~ v2exl_legitideol, family  = binomial(link = "logit"), data = autocracies_data)
summary(hurdle_part_ideo)
exp(coef(hurdle_part_ideo))

## Exponentiated coefficients
expCoef <- exp(coef((model_ideo_hurdle)))
expCoef <- matrix(expCoef, ncol = 2)
rownames(expCoef) <- names(coef(hurdle_part_ideo))
colnames(expCoef) <- c("Count_model","Zero_hurdle_model")
expCoef




```

### Models for hypotheses

#### H1 Regimes with higher levels of opposition are more likely to support NAGS, all else equal

```{r echo=FALSE}

formulah1 <- NumNAG_S ~ oppsize_norm + WarOnTerror + ColdWar + capdist

formulah1b <- Num_S_TrainCamp ~ oppsize_norm + WarOnTerror + ColdWar + capdist
        
        
#Poisson model using Number of groups supported

h1_numS <- glm(formula = formulah1, family  = poisson(link = "log"), data = autocracies_data)
summary(h1_numS)
exp(coef(h1_numS))

# quasipoisson model using number of groups supported

h1_numSq <- glm(formula = formulah1, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h1_numSq)
exp(coef(h1_numSq))

# negative binomial model using number of groups supported

h1_numSnb <- glm.nb(formula = formulah1, data = autocracies_data)
summary(h1_numSnb)
exp(coef(h1_numSnb))


# Hurdle model

h1_hurdle <- hurdle(formula = formulah1, data = autocracies_data)
summary(h1_hurdle)

h1_hurdle_part <- glm(I(NumNAG_S>0) ~ oppsize_norm + WarOnTerror + ColdWar + capdist, family  = binomial(link = "logit"), data = autocracies_data)
summary(h1_hurdle_part)
exp(coef(h1_hurdle_part))



#Model using number of groups with training camps in country
#

#Poisson model using Number of groups with training camps in country

h1_numSb <- glm(formula = formulah1b, family  = poisson(link = "log"), data = autocracies_data)
summary(h1_numSb)
exp(coef(h1_numSb))

# quasipoisson model using number of groups supported

h1_numSqb <- glm(formula = formulah1b, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h1_numSqb)
exp(coef(h1_numSqb))

# negative binomial model using number of groups supported

h1_numSnbb <- glm.nb(formula = formulah1b, data = autocracies_data)
summary(h1_numSnbb)
exp(coef(h1_numSnbb))


# Hurdle model

h1_hurdleb <- hurdle(formula = formulah1b, data = autocracies_data)
summary(h1_hurdleb)

h1_hurdle_partb <- glm(I(Num_S_TrainCamp>0) ~ oppsize_norm + WarOnTerror + ColdWar + capdist, family  = binomial(link = "logit"), data = autocracies_data)
summary(h1_hurdle_partb)
exp(coef(h1_hurdle_partb))

library(stargazer)
stargazer(h1_hurdle, type = "text")
stargazer(h1_hurdleb, type = "text")

cat("\n h1_hurdle - number supported \n")

## Exponentiated coefficients
expCoefh1 <- exp(coef((h1_hurdle)))
expCoefh1 <- matrix(expCoefh1, ncol = 2)
rownames(expCoefh1) <- names(coef(h1_hurdle_part))
colnames(expCoefh1) <- c("Count_model","Zero_hurdle_model")
expCoefh1

cat("\n h1_hurdle - number with training camps \n")

## Exponentiated coefficients
expCoefh1b <- round(exp(coef((h1_hurdleb))), digits = 5)
expCoefh1b <- matrix(expCoefh1b, ncol = 2)
rownames(expCoefh1b) <- names(coef(h1_hurdle_partb))
colnames(expCoefh1b) <- c("Count_model","Zero_hurdle_model")
expCoefh1b

```
#### H2: Regimes with higher levels of opposition are more likely to support NAGS that target democracies, all else equal

```{r echo=FALSE}

formulah2 <- NumNAG_S ~ targ_democratic * oppsize_norm + WarOnTerror + ColdWar + capdist

formulah2b <- Num_S_TrainCamp ~ targ_democratic * oppsize_norm + WarOnTerror + ColdWar + capdist

#Poisson model using Number of groups supported

h2_numS <- glm(formula = formulah2, family  = poisson(link = "log"), data = autocracies_data)
summary(h2_numS)
exp(coef(h2_numS))

# quasipoisson model using number of groups supported

h2_numSq <- glm(formula = formulah2, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h2_numSq)
exp(coef(h2_numSq))

# negative binomial model using number of groups supported

h2_numSnb <- glm.nb(formula = formulah2, data = autocracies_data)
summary(h2_numSnb)
exp(coef(h2_numSnb))


# Hurdle model

h2_hurdle <- hurdle(formula = formulah2, data = autocracies_data)
summary(h2_hurdle)

h2_hurdle_part <- glm(I(NumNAG_S>0) ~ targ_democratic * oppsize_norm + WarOnTerror + ColdWar + capdist, family  = binomial(link = "logit"), data = autocracies_data)
summary(h2_hurdle_part)
exp(coef(h2_hurdle_part))

#Model using number of groups with training camps in country
#

#Poisson model using Number of groups with training camps in country

h2_numSb <- glm(formula = formulah2b, family  = poisson(link = "log"), data = autocracies_data)
summary(h2_numSb)
exp(coef(h2_numSb))

# quasipoisson model using number of groups supported

h2_numSqb <- glm(formula = formulah2b, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h2_numSqb)
exp(coef(h2_numSqb))

# negative binomial model using number of groups supported

h2_numSnbb <- glm.nb(formula = formulah2b, data = autocracies_data)
summary(h2_numSnbb)
exp(coef(h2_numSnbb))


# Hurdle model

h2_hurdleb <- hurdle(formula = formulah2b, data = autocracies_data)
summary(h2_hurdleb)

h2_hurdle_partb <- glm(I(Num_S_TrainCamp>0) ~ targ_democratic * oppsize_norm + WarOnTerror + ColdWar + capdist, family  = binomial(link = "logit"), data = autocracies_data)
summary(h2_hurdle_partb)
exp(coef(h2_hurdle_partb))


stargazer(h2_hurdle, type = "text")
stargazer(h2_hurdleb, type = "text")

cat("h2_hurdle - number supported \n")

## Exponentiated coefficients
expCoefh2 <- exp(coef((h2_hurdle)))
expCoefh2 <- matrix(expCoefh2, ncol = 2)
rownames(expCoefh2) <- names(coef(h2_hurdle_part))
colnames(expCoefh2) <- c("Count_model","Zero_hurdle_model")
expCoefh2


cat("\n h2_hurdle - number with training camps \n")

## Exponentiated coefficients
expCoefh2b <- round(exp(coef((h2_hurdleb))), digits = 5)
expCoefh2b <- matrix(expCoefh2b, ncol = 2)
rownames(expCoefh2b) <- names(coef(h2_hurdle_partb))
colnames(expCoefh2b) <- c("Count_model","Zero_hurdle_model")
expCoefh2b

```


#### H3 Regimes with lower levels of military capability are more likely to support NAGS, all else equal


```{r echo=FALSE}

formulah3 <- NumNAG_S ~ milpercap_norm + WarOnTerror + ColdWar   + capdist

formulah3b <- Num_S_TrainCamp ~ milpercap_norm + WarOnTerror + ColdWar   + capdist

#Poisson model using Number of groups supported

h3_numS <- glm(formula = formulah3, family  = poisson(link = "log"), data = autocracies_data)
summary(h3_numS)
exp(coef(h3_numS))

# quasipoisson model using number of groups supported

h3_numSq <- glm(formula = formulah3, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h3_numSq)
exp(coef(h3_numSq))

# negative binomial model using number of groups supported

h3_numSnb <- glm.nb(formula = formulah3, data = autocracies_data)
summary(h3_numSnb)
exp(coef(h3_numSnb))


# Hurdle model

h3_hurdle <- hurdle(formula = formulah3, data = autocracies_data)
summary(h3_hurdle)

h3_hurdle_part <- glm(I(NumNAG_S>0) ~ milpercap_norm + WarOnTerror + ColdWar   + capdist, family  = binomial(link = "logit"), data = autocracies_data)
summary(h3_hurdle_part)
exp(coef(h3_hurdle_part))

## Exponentiated coefficients
expCoefh3 <- exp(coef((h3_hurdle)))
expCoefh3 <- matrix(expCoefh3, ncol = 2)
rownames(expCoefh3) <- names(coef(h3_hurdle_part))
colnames(expCoefh3) <- c("Count_model","Zero_hurdle_model")
expCoefh3


#Model using number of groups with training camps in country
#

#Poisson model using Number of groups with training camps in country

h3_numSb <- glm(formula = formulah3b, family  = poisson(link = "log"), data = autocracies_data)
summary(h3_numSb)
exp(coef(h3_numSb))

# quasipoisson model using number of groups supported

h3_numSqb <- glm(formula = formulah3b, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h3_numSqb)
exp(coef(h3_numSqb))

# negative binomial model using number of groups supported

h3_numSnbb <- glm.nb(formula = formulah3b, data = autocracies_data)
summary(h3_numSnbb)
exp(coef(h3_numSnbb))


# Hurdle model

h3_hurdleb <- hurdle(formula = formulah3b, data = autocracies_data)
summary(h3_hurdleb)

h3_hurdle_partb <- glm(I(Num_S_TrainCamp>0) ~ milpercap_norm + WarOnTerror + ColdWar   + capdist, family  = binomial(link = "logit"), data = autocracies_data)
summary(h3_hurdle_partb)
exp(coef(h3_hurdle_partb))



cat("\n h3_hurdle - number supported \n")

## Exponentiated coefficients
expCoefh3 <- exp(coef((h3_hurdle)))
expCoefh3 <- matrix(expCoefh3, ncol = 2)
rownames(expCoefh3) <- names(coef(h3_hurdle_part))
colnames(expCoefh3) <- c("Count_model","Zero_hurdle_model")
expCoefh3

cat("\n h3_hurdle - number with training camps \n")

## Exponentiated coefficients
expCoefh3b <- round(exp(coef((h3_hurdleb))), digits = 5)
expCoefh3b <- matrix(expCoefh3b, ncol = 2)
rownames(expCoefh3b) <- names(coef(h3_hurdle_partb))
colnames(expCoefh3b) <- c("Count_model","Zero_hurdle_model")
expCoefh3b


```


#### H4 Regimes with lower levels of millitary capability are more likely to support NAGs that target democracies, all else equal

```{r echo=FALSE}

formulah4 <- NumNAG_S ~ targ_democratic * milpercap_norm + WarOnTerror + ColdWar   + capdist

formulah4b <- Num_S_TrainCamp ~ targ_democratic * milpercap_norm + WarOnTerror + ColdWar   + capdist

#Poisson model using Number of groups supported

h4_numS <- glm(formula = formulah4, family  = poisson(link = "log"), data = autocracies_data)
summary(h4_numS)
exp(coef(h4_numS))

# quasipoisson model using number of groups supported

h4_numSq <- glm(formula = formulah4, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h4_numSq)
exp(coef(h4_numSq))

# negative binomial model using number of groups supported

h4_numSnb <- glm.nb(formula = formulah4, data = autocracies_data)
summary(h4_numSnb)
exp(coef(h4_numSnb))


# Hurdle model

h4_hurdle <- hurdle(formula = formulah4, data = autocracies_data)
summary(h4_hurdle)

h4_hurdle_part <- glm(I(NumNAG_S>0) ~ targ_democratic * milpercap_norm + WarOnTerror + ColdWar   + capdist, family  = binomial(link = "logit"), data = autocracies_data)
summary(h4_hurdle_part)
exp(coef(h4_hurdle_part))

## Exponentiated coefficients
expCoefh4 <- exp(coef((h4_hurdle)))
expCoefh4 <- matrix(expCoefh4, ncol = 2)
rownames(expCoefh4) <- names(coef(h4_hurdle_part))
colnames(expCoefh4) <- c("Count_model","Zero_hurdle_model")
expCoefh4


#Model using number of groups with training camps in country
#

#Poisson model using Number of groups with training camps in country

h4_numSb <- glm(formula = formulah4b, family  = poisson(link = "log"), data = autocracies_data)
summary(h4_numSb)
exp(coef(h4_numSb))

# quasipoisson model using number of groups supported

h4_numSqb <- glm(formula = formulah4b, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h4_numSqb)
exp(coef(h4_numSqb))

# negative binomial model using number of groups supported

h4_numSnbb <- glm.nb(formula = formulah4b, data = autocracies_data)
summary(h4_numSnbb)
exp(coef(h4_numSnbb))


# Hurdle model

h4_hurdleb <- hurdle(formula = formulah4b, data = autocracies_data)
summary(h4_hurdleb)

h4_hurdle_partb <- glm(I(Num_S_TrainCamp>0) ~ targ_democratic * milpercap_norm + WarOnTerror + ColdWar   + capdist, family  = binomial(link = "logit"), data = autocracies_data)
summary(h4_hurdle_partb)
exp(coef(h4_hurdle_partb))

cat("\n h4_hurdle - number supported \n")

## Exponentiated coefficients
expCoefh4 <- exp(coef((h4_hurdle)))
expCoefh4 <- matrix(expCoefh4, ncol = 2)
rownames(expCoefh4) <- names(coef(h4_hurdle_part))
colnames(expCoefh4) <- c("Count_model","Zero_hurdle_model")
expCoefh4

cat("\n h4_hurdle - number with training camps \n")

## Exponentiated coefficients
## 

expCoefh4b <- round(exp(coef((h4_hurdleb))), digits = 4)
expCoefh4b <- matrix(expCoefh4b, ncol = 2)
rownames(expCoefh4b) <- names(coef(h4_hurdle_partb))
colnames(expCoefh4b) <- c("Count_model","Zero_hurdle_model")
expCoefh4b



```
#### H5 Regimes with lower levels of state capacity are more likely to support NAGS, all else equal. 
                
         

```{r echo=FALSE}

formulah5 <- NumNAG_S ~ capacity + WarOnTerror + ColdWar   + capdist

formulah5b <- Num_S_TrainCamp ~ capacity + WarOnTerror + ColdWar   + capdist

#Poisson model using Number of groups supported

h5_numS <- glm(formula = formulah5, family  = poisson(link = "log"), data = autocracies_data)
summary(h5_numS)
exp(coef(h5_numS))

# quasipoisson model using number of groups supported

h5_numSq <- glm(formula = formulah5, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h5_numSq)
exp(coef(h5_numSq))

# negative binomial model using number of groups supported

h5_numSnb <- glm.nb(formula = formulah5, data = autocracies_data)
summary(h5_numSnb)
exp(coef(h5_numSnb))


# Hurdle model

h5_hurdle <- hurdle(formula = formulah5, data = autocracies_data)
summary(h5_hurdle)

h5_hurdle_part <- glm(I(NumNAG_S>0) ~ capacity + WarOnTerror + ColdWar   + capdist, family  = binomial(link = "logit"), data = autocracies_data)
summary(h5_hurdle_part)
exp(coef(h5_hurdle_part))

## Exponentiated coefficients
expCoefh5 <- exp(coef((h5_hurdle)))
expCoefh5 <- matrix(expCoefh5, ncol = 2)
rownames(expCoefh5) <- names(coef(h5_hurdle_part))
colnames(expCoefh5) <- c("Count_model","Zero_hurdle_model")
expCoefh5


#Model using number of groups with training camps in country
#

#Poisson model using Number of groups with training camps in country

h5_numSb <- glm(formula = formulah5b, family  = poisson(link = "log"), data = autocracies_data)
summary(h5_numSb)
exp(coef(h5_numSb))

# quasipoisson model using number of groups supported

h5_numSqb <- glm(formula = formulah5b, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h5_numSqb)
exp(coef(h5_numSqb))

# negative binomial model using number of groups supported

h5_numSnbb <- glm.nb(formula = formulah5b, data = autocracies_data)
summary(h5_numSnbb)
exp(coef(h5_numSnbb))


# Hurdle model

h5_hurdleb <- hurdle(formula = formulah5b, data = autocracies_data)
summary(h5_hurdleb)

h5_hurdle_partb <- glm(I(Num_S_TrainCamp>0) ~ capacity + WarOnTerror + ColdWar   + capdist, family  = binomial(link = "logit"), data = autocracies_data)
summary(h5_hurdle_partb)
exp(coef(h5_hurdle_partb))


cat("\n h5_hurdle - number supported \n")

## Exponentiated coefficients
expCoefh5 <- exp(coef((h5_hurdle)))
expCoefh5 <- matrix(expCoefh5, ncol = 2)
rownames(expCoefh5) <- names(coef(h5_hurdle_part))
colnames(expCoefh5) <- c("Count_model","Zero_hurdle_model")
expCoefh5

cat("\n h5_hurdle - number with camps \n")

## Exponentiated coefficients
expCoefh5b <- round(exp(coef((h5_hurdleb))), digits = 5)
expCoefh5b <- matrix(expCoefh5b, ncol = 2)
rownames(expCoefh5b) <- names(coef(h5_hurdle_partb))
colnames(expCoefh5b) <- c("Count_model","Zero_hurdle_model")
expCoefh5b


```


#### H6 Regimes with lower levels of state capacity are more likely to support NAGS that target democracies, all else equal.      

```{r echo=FALSE}

formulah6 <- NumNAG_S ~ targ_democratic * capacity + WarOnTerror + ColdWar   + capdist

formulah6b <- Num_S_TrainCamp ~ targ_democratic * capacity + WarOnTerror + ColdWar   + capdist

#Poisson model using Number of groups supported

h6_numS <- glm(formula = formulah6, family  = poisson(link = "log"), data = autocracies_data)
summary(h6_numS)
exp(coef(h6_numS))

# quasipoisson model using number of groups supported

h6_numSq <- glm(formula = formulah6, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h6_numSq)
exp(coef(h6_numSq))

# negative binomial model using number of groups supported

h6_numSnb <- glm.nb(formula = formulah6, data = autocracies_data)
summary(h6_numSnb)
exp(coef(h6_numSnb))


# Hurdle model

h6_hurdle <- hurdle(formula = formulah6, data = autocracies_data)
summary(h6_hurdle)

h6_hurdle_part <- glm(I(NumNAG_S>0) ~ targ_democratic * capacity + WarOnTerror + ColdWar   + capdist, family  = binomial(link = "logit"), data = autocracies_data)
summary(h6_hurdle_part)
exp(coef(h6_hurdle_part))


cat("\n h6_hurdle - number supported \n")

cat("\n h6_hurdle - number with camps \n")

## Exponentiated coefficients
expCoefh6 <- exp(coef((h6_hurdle)))
expCoefh6 <- matrix(expCoefh6, ncol = 2)
rownames(expCoefh6) <- names(coef(h6_hurdle_part))
colnames(expCoefh6) <- c("Count_model","Zero_hurdle_model")
expCoefh6


#Model using number of groups with training camps in country
#

#Poisson model using Number of groups with training camps in country

h6_numSb <- glm(formula = formulah6b, family  = poisson(link = "log"), data = autocracies_data)
summary(h6_numSb)
exp(coef(h6_numSb))

# quasipoisson model using number of groups supported

h6_numSqb <- glm(formula = formulah6b, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h6_numSqb)
exp(coef(h6_numSqb))

# negative binomial model using number of groups supported

h6_numSnbb <- glm.nb(formula = formulah6b, data = autocracies_data)
summary(h6_numSnbb)
exp(coef(h6_numSnbb))


# Hurdle model

h6_hurdleb <- hurdle(formula = formulah6b, data = autocracies_data)
summary(h6_hurdleb)

h6_hurdle_partb <- glm(I(Num_S_TrainCamp>0) ~ targ_democratic * capacity + WarOnTerror + ColdWar   + capdist, family  = binomial(link = "logit"), data = autocracies_data)
summary(h6_hurdle_partb)
exp(coef(h6_hurdle_partb))




cat("\n h6_hurdle - number supported \n")



## Exponentiated coefficients
expCoefh6 <- exp(coef((h6_hurdle)))
expCoefh6 <- matrix(expCoefh6, ncol = 2)
rownames(expCoefh6) <- names(coef(h6_hurdle_part))
colnames(expCoefh6) <- c("Count_model","Zero_hurdle_model")
expCoefh6
## Exponentiated coefficients
## 

cat("\n h6_hurdle - number with camps \n")

expCoefh6b <- round(exp(coef((h6_hurdleb))), digits = 4)
expCoefh6b <- matrix(expCoefh6b, ncol = 2)
rownames(expCoefh6b) <- names(coef(h6_hurdle_partb))
colnames(expCoefh6b) <- c("Count_model","Zero_hurdle_model")
expCoefh6b



```


## Drop Soviet Union and China and re-run H3 and H4

```{r}

new_autocracies_data <- autocracies_data[which(autocracies_data$SupNum_COW != 365 & autocracies_data$SupNum_COW != 710),]

formulah3n <- NumNAG_S ~ milpercap_norm + WarOnTerror + ColdWar   + capdist

formulah3nb <- Num_S_TrainCamp ~ milpercap_norm + WarOnTerror + ColdWar   + capdist

#Poisson model using Number of groups supported

h3n_numS <- glm(formula = formulah3n, family  = poisson(link = "log"), data = new_autocracies_data)
summary(h3n_numS)
exp(coef(h3n_numS))

# quasipoisson model using number of groups supported

h3n_numSq <- glm(formula = formulah3n, family  = quasipoisson(link = "log"), data = new_autocracies_data)
summary(h3n_numSq)
exp(coef(h3n_numSq))

# negative binomial model using number of groups supported

h3n_numSnb <- glm.nb(formula = formulah3n, data = new_autocracies_data)
summary(h3n_numSnb)
exp(coef(h3n_numSnb))


# Hurdle model

h3n_hurdle <- hurdle(formula = formulah3n, data = new_autocracies_data)
summary(h3n_hurdle)

h3n_hurdle_part <- glm(I(NumNAG_S>0) ~ milpercap_norm + WarOnTerror + ColdWar   + capdist, family  = binomial(link = "logit"), data = new_autocracies_data)
summary(h3n_hurdle_part)
exp(coef(h3n_hurdle_part))

## Exponentiated coefficients
expCoefh3n <- exp(coef((h3n_hurdle)))
expCoefh3n <- matrix(expCoefh3n, ncol = 2)
rownames(expCoefh3n) <- names(coef(h3n_hurdle_part))
colnames(expCoefh3n) <- c("Count_model","Zero_hurdle_model")
expCoefh3n


#Model using number of groups with training camps in country
#

#Poisson model using Number of groups with training camps in country

h3n_numSb <- glm(formula = formulah3nb, family  = poisson(link = "log"), data = new_autocracies_data)
summary(h3n_numSb)
exp(coef(h3n_numSb))

# quasipoisson model using number of groups supported

h3n_numSqb <- glm(formula = formulah3nb, family  = quasipoisson(link = "log"), data = new_autocracies_data)
summary(h3n_numSqb)
exp(coef(h3n_numSqb))

# negative binomial model using number of groups supported

h3n_numSnbb <- glm.nb(formula = formulah3nb, data = new_autocracies_data)
summary(h3n_numSnbb)
exp(coef(h3n_numSnbb))


# Hurdle model

h3n_hurdleb <- hurdle(formula = formulah3nb, data = new_autocracies_data)
summary(h3n_hurdleb)

h3n_hurdle_partb <- glm(I(Num_S_TrainCamp>0) ~ milpercap_norm + WarOnTerror + ColdWar   + capdist, family  = binomial(link = "logit"), data = new_autocracies_data)
summary(h3n_hurdle_partb)
exp(coef(h3n_hurdle_partb))

## Exponentiated coefficients
expCoefh3nb <- round(exp(coef((h3n_hurdleb))), digits = 5)
expCoefh3nb <- matrix(expCoefh3nb, ncol = 2)
rownames(expCoefh3nb) <- names(coef(h3n_hurdle_partb))
colnames(expCoefh3nb) <- c("Count_model","Zero_hurdle_model")
expCoefh3nb


formulah4n <- NumNAG_S ~ targ_democratic * milpercap_norm + WarOnTerror + ColdWar   + capdist

formulah4nb <- Num_S_TrainCamp ~ targ_democratic * milpercap_norm + WarOnTerror + ColdWar   + capdist

#Poisson model using Number of groups supported

h4n_numS <- glm(formula = formulah4n, family  = poisson(link = "log"), data = new_autocracies_data)
summary(h4n_numS)
exp(coef(h4n_numS))

# quasipoisson model using number of groups supported

h4n_numSq <- glm(formula = formulah4n, family  = quasipoisson(link = "log"), data = new_autocracies_data)
summary(h4n_numSq)
exp(coef(h4n_numSq))

# negative binomial model using number of groups supported

h4n_numSnb <- glm.nb(formula = formulah4n, data = new_autocracies_data)
summary(h4n_numSnb)
exp(coef(h4n_numSnb))


# Hurdle model

h4n_hurdle <- hurdle(formula = formulah4n, data = new_autocracies_data)
summary(h4n_hurdle)

h4n_hurdle_part <- glm(I(NumNAG_S>0) ~ targ_democratic * milpercap_norm + WarOnTerror + ColdWar   + capdist, family  = binomial(link = "logit"), data = new_autocracies_data)
summary(h4n_hurdle_part)
exp(coef(h4n_hurdle_part))

## Exponentiated coefficients
expCoefh4n <- exp(coef((h4n_hurdle)))
expCoefh4n <- matrix(expCoefh4n, ncol = 2)
rownames(expCoefh4n) <- names(coef(h4n_hurdle_part))
colnames(expCoefh4n) <- c("Count_model","Zero_hurdle_model")
expCoefh4n


#Model using number of groups with training camps in country
#

#Poisson model using Number of groups with training camps in country

h4n_numSb <- glm(formula = formulah4nb, family  = poisson(link = "log"), data = new_autocracies_data)
summary(h4n_numSb)
exp(coef(h4n_numSb))

# quasipoisson model using number of groups supported

h4n_numSqb <- glm(formula = formulah4nb, family  = quasipoisson(link = "log"), data = new_autocracies_data)
summary(h4n_numSqb)
exp(coef(h4n_numSqb))

# negative binomial model using number of groups supported

h4n_numSnbb <- glm.nb(formula = formulah4nb, data = new_autocracies_data)
summary(h4n_numSnbb)
exp(coef(h4n_numSnbb))


# Hurdle model

h4n_hurdleb <- hurdle(formula = formulah4nb, data = new_autocracies_data)
summary(h4n_hurdleb)

h4n_hurdle_partb <- glm(I(Num_S_TrainCamp>0) ~ targ_democratic * milpercap_norm + WarOnTerror + ColdWar   + capdist, family  = binomial(link = "logit"), data = new_autocracies_data)
summary(h4n_hurdle_partb)
exp(coef(h4n_hurdle_partb))



## Exponentiated coefficients
## 

expCoefh4nb <- round(exp(coef((h4n_hurdleb))), digits = 4)
expCoefh4nb <- matrix(expCoefh4nb, ncol = 2)
rownames(expCoefh4nb) <- names(coef(h4n_hurdle_partb))
colnames(expCoefh4nb) <- c("Count_model","Zero_hurdle_model")
expCoefh4nb



```


             


#### H5 If regimes substitute NAGS for repression, regimes with lower levels of repression are more likely to support NAGS, all else equal.
             
#### H6 If signals are successful, regimes with higher support for NAGS will have lower levels of protest 




```{r echo=FALSE}


library(MASS)
library(pscl)


## model on legitimation by ideology autocracies only
## 


model_ideo <- glm(NumNAG_S ~ v2exl_legitideol, family  = poisson(link = "log"), data = autocracies_data)
summary(model_ideo)
exp(coef(model_ideo))

model_ideo_qp <- glm(NumNAG_S ~ v2exl_legitideol, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(model_ideo_qp)
exp(coef(model_ideo_qp))


model_ideo_hurdle <- hurdle(NumNAG_S ~ v2exl_legitideol | v2exl_legitideol, data = autocracies_data)
summary(model_ideo_hurdle)


## model on full data with just target democracy variable
## 

model_base <- glm.nb(NumNAG_S ~ targ_democratic, data = full_data)
summary(model_base)

# model base with control for time period variables

model_basec <- glm.nb(NumNAG_S ~ targ_democratic + WarOnTerror + ColdWar, data = full_data)
summary(model_basec)

## model base with supporter democratic or non-democratic

model_based <- glm.nb(NumNAG_S ~ targ_democratic + supp_democratic + WarOnTerror + ColdWar, data = full_data)
summary(model_based)

# models with just opposition and support group sizes
# 

model_opposition <- glm.nb(NumNAG_S ~ targ_democratic + oppsize_norm + WarOnTerror + ColdWar, data = autocracies_data)
summary(model_opposition)

model_oppositionTrainCamp <- glm.nb(Num_S_TrainCamp ~ targ_democratic + oppsize_norm + WarOnTerror + ColdWar, data = autocracies_data)
summary(model_oppositionTrainCamp)


model_support <- glm.nb(NumNAG_S ~ targ_democratic + suppsize_norm +  WarOnTerror + ColdWar, data = autocracies_data)
summary(model_support)

model_supportTrainCamp <- glm.nb(Num_S_TrainCamp ~ targ_democratic + suppsize_norm + WarOnTerror + ColdWar, data = autocracies_data)
summary(model_supportTrainCamp)
        


## Model W - just the effect of W
## 


modelWTrainCamp <- glm.nb(Num_S_TrainCamp ~ targ_democratic + W_norm + WarOnTerror + ColdWar, data = autocracies_data)
summary(modelWTrainCamp)

#ratio of actual support to W - how close are they to a truly minimal winning coalition
#
model1TrainCamp <- glm.nb(Num_S_TrainCamp ~ targ_democratic + supp_W_ratio + WarOnTerror + ColdWar, data = autocracies_data)
summary(model1TrainCamp)


# ratio of opponent size to W - how close are the opposition to having a minimal winning coalition of their own

model2TrainCamp <-  glm.nb(Num_S_TrainCamp ~ targ_democratic + opp_W_ratio + WarOnTerror + ColdWar, data = autocracies_data)
summary(model2TrainCamp)



# ratio of opposition to supporters - head to head match up
# 

model3TrainCamp <- glm.nb(Num_S_TrainCamp ~ targ_democratic + opp_supp_ratio + WarOnTerror + ColdWar, data = autocracies_data)
summary(model3TrainCamp)


## multivariate model - ideology, opp_supp_ratio, strategic variables
##  v2exl_legitideol

modelmulti_traincamp <- glm.nb(Num_S_TrainCamp ~ targ_democratic + opp_supp_ratio + v2exl_legitideol + WarOnTerror + ColdWar + supporter_milex + target_milex, data = autocracies_data)
summary(modelmulti_traincamp)

modelmulti_traincamp2 <- glm.nb(Num_S_TrainCamp ~ targ_democratic + opp_supp_ratio + v2exl_legitideol + WarOnTerror + ColdWar  , data = autocracies_data)
summary(modelmulti_traincamp2)



```



## Model Tables, Plots and Predictions

```{r echo=FALSE}

cat("Hypothesis H1 with number armed groups")

expCoefh1

coef(summary(h1_hurdle_part))[,"z value"]

cat("Hypothesis H1 with number with training camps")

expCoefh1b

cat("Hypothesis H2 with number armed groups")

expCoefh2

cat("Hypothesis H2 with number with training camps")

expCoefh2b

cat("Hypothesis H3 with number armed groups")

expCoefh3

cat("Hypothesis H3 with number with training camps")

expCoefh3b

cat("Hypothesis H4 with number armed groups")

expCoefh4

cat("Hypothesis H4 with number with training camps")

expCoefh4b

cat("Hypothesis H5 with number armed groups")

expCoefh5

cat("Hypothesis H5 with number with training camps")

expCoefh5b

cat("Hypothesis H6 with number armed groups")

expCoefh6

cat("Hypothesis H6 with number with training camps")

expCoefh6b



```


