---
title: "R Notebook"
output:
  html_document:
    df_print: paged
---

```{r echo = FALSE}

options(scipen=999)

#Loading NAGS dyadic (supporter-target) data

library(here)
library(readr)
nags_data1 <- read_delim(here("data","Dyadic_Target-Supporter_active_support.csv"), delim = ";", escape_double = FALSE, trim_ws = TRUE)


nags_data1 <- nags_data1[which(nags_data1$Year > 1945),]

nags_data1$year <- nags_data1$Year
nags_data1$COWcode <- nags_data1$SupNum_COW

head(nags_data1)

```

```{r echo=FALSE}

# creating polity scores for supporter and target countries

#load polity data set for suppoters
#
library(readxl)
support_polity <- read_excel("data/p5v2018.xls")
head(support_polity)

#create score labels for supporters
support_polity$supporter_p5 <- support_polity$p5
support_polity$supporter_cyear <- support_polity$cyear
support_polity$supporter_flag <- support_polity$flag
support_polity$SupNum_COW <- support_polity$ccode 
support_polity$supporter_democ <- support_polity$democ 
support_polity$supporter_autoc <- support_polity$autoc
support_polity$supporter_polity <- support_polity$polity
support_polity$supporter_polity2 <- support_polity$polity2
support_polity$supporter_durable <- support_polity$durable

#select only the supporter named variables

support_polity <- support_polity[c(6,38:46)]

#repeat the above for target countries

#load polity data set for targets
#
target_polity <- read_excel("data/p5v2018.xls")
head(target_polity)

#create score labels for targets
target_polity$target_p5 <- target_polity$p5
target_polity$target_cyear <- target_polity$cyear
target_polity$target_flag <- target_polity$flag
target_polity$TarNum_COW <- target_polity$ccode 
target_polity$target_democ <- target_polity$democ 
target_polity$target_autoc <- target_polity$autoc
target_polity$target_polity <- target_polity$polity
target_polity$target_polity2 <- target_polity$polity2
target_polity$target_durable <- target_polity$durable

#select only the target named variables

target_polity <- target_polity[c(6,38:46)]


```

```{r echo=FALSE}
# Merge polity data for supporters
library(dplyr)
nags_data1 <- left_join(nags_data1,support_polity, by = c("SupNum_COW","year"))

# Merge polity data for targets

nags_data1 <- left_join(nags_data1,target_polity, by = c("TarNum_COW","year"))

# add national capabilities data for supporters and targets

# load national material capabilities data
# 

NMC<- read_csv(here("data","NMC-60-abridged.csv"))
head(NMC)

NMC$COWcode <- NMC$ccode

NMC <- NMC[which(NMC$year > 1945 & NMC$year < 2011),]

NMC <- NMC[c(3:12)]

NMC_supp <- NMC

NMC_supp$SupNum_COW <- NMC_supp$COWcode
NMC_supp$supporter_milex <- NMC_supp$milex
NMC_supp$supporter_milper <- NMC_supp$milper
NMC_supp$supporter_irst <- NMC_supp$irst
NMC_supp$supporter_pec <- NMC_supp$pec
NMC_supp$supporter_tpop <- NMC_supp$tpop
NMC_supp$supporter_upop <- NMC_supp$upop
NMC_supp$supporter_cinc <- NMC_supp$cinc

NMC_supp <- NMC_supp[c(1,11:18)]

NMC_targ <- NMC

NMC_targ$TarNum_COW <- NMC_targ$COWcode
NMC_targ$target_milex <- NMC_targ$milex
NMC_targ$target_milper <- NMC_targ$milper
NMC_targ$target_irst <- NMC_targ$irst
NMC_targ$target_pec <- NMC_targ$pec
NMC_targ$target_tpop <- NMC_targ$tpop
NMC_targ$target_upop <- NMC_targ$upop
NMC_targ$target_cinc <- NMC_targ$cinc

NMC_targ <- NMC_targ[c(1,11:18)]

nags_data1 <- left_join(nags_data1,NMC_supp, by = c("SupNum_COW","year"))

nags_data1 <- left_join(nags_data1,NMC_targ, by = c("TarNum_COW","year"))


```



```{r echo=FALSE}

countries_data <- read_csv(here("data","vdem_plus_w.csv"))
head(countries_data)

countries_data <- countries_data[which(countries_data$year < 2011),]

library(dplyr)

full_data <- left_join(nags_data1,countries_data, by = c("COWcode","year"))

# vdem_select1 <- vdem_w_select[which(vdem_w_select$year > 1945),]




```


## To Do (variables)

                + Use Cshapes to add minimum distance between states in dyad - done
                + Use Cshapes to add distance between capitals in dyad - done
                + Add variable for violent repression (PTS data has limitations - only post-1976 and includes all state violence not just political repression)
                
## Additional Sources

                + For protests, riots, and violence against civilians)
                (https://acleddata.com/data-export-tool/
                + For general levels of poltical terror - Political Terror Scale


```{r echo=FALSE}
# summary(full_data$W_norm)

# create a democracy target variable
# 


full_data$targ_democratic <- ifelse(full_data$target_polity > 6,1,0)
# summary(full_data$targ_democratic)

#create a binary democracy variable for supporters 

full_data$supp_democratic <- ifelse(full_data$supporter_polity > 6,1,0)
# summary(full_data$supp_democratic)




# normalize opposition and support group size variables
# 


minopp <- min(full_data$v2regoppgroupssize, na.rm = TRUE)
maxopp <- max(full_data$v2regoppgroupssize, na.rm = TRUE)


full_data$oppsize_norm <- (full_data$v2regoppgroupssize - minopp ) / (maxopp - minopp)


minsupp <- min(full_data$v2regsupgroupssize, na.rm = TRUE)
maxsupp <- max(full_data$v2regsupgroupssize, na.rm = TRUE)

full_data$suppsize_norm <- (full_data$v2regsupgroupssize - minsupp) / (maxsupp - minsupp)


summary(full_data$suppsize_norm)
summary(full_data$oppsize_norm)



# create a variable of ratio of opposition to support group size

full_data$opp_supp_ratio <- full_data$oppsize_norm / full_data$suppsize_norm
# summary(full_data$opp_supp_ratio)

# create variable of ratio of support size score to W score
# 

full_data$supp_W_ratio <- full_data$suppsize_norm / full_data$W_norm
# summary(full_data$supp_W_ratio)


# create variable of ratio of opposition to W

full_data$opp_W_ratio <- full_data$oppsize_norm / full_data$W_norm
# summary(full_data$opp_W_ratio)


# create variables for Cold War and War on Terror (post-911)

full_data$ColdWar <- ifelse(full_data$year < 1991,1,0)
# summary(full_data$ColdWar)

full_data$WarOnTerror <- ifelse(full_data$year > 2001,1,0)
# summary(full_data$WarOnTerror)


## use cshapes data to include minimum distance and distance between capitals
## 

library(cshapes)

#create a vector of dates for years in data set

cap_dist <- distlist(date = as.Date("2010-01-01"), type = "capdist", useGW = FALSE)

cap_dist$SupNum_COW <- cap_dist$ccode1
cap_dist$TarNum_COW <- cap_dist$ccode2
cap_dist <- cap_dist[c(3:5)]

# min_dist <- distlist(date = as.Date("2010-01-01"), type = "mindist", useGW = FALSE)
# 
# min_dist$SupNum_COW <- min_dist$ccode1
# min_dist$TarNum_COW <- min_dist$ccode2
# min_dist <- min_dist[c(3:5)]
# 
# write.csv(min_dist, file = here("data","min_dist.csv"))
# 

min_dist <- read_csv(here("data","min_dist.csv"))
min_dist <- min_dist[c(2:4)]

full_data <- left_join(full_data,cap_dist, by = c("SupNum_COW","TarNum_COW"))

full_data <- left_join(full_data,min_dist, by = c("SupNum_COW","TarNum_COW"))

#create binary variable for autocracy (used later to create subsets)
full_data$supp_autocratic <- ifelse(full_data$supporter_polity < -5,1,0)


# Political Terror Scale data
# 

pts <- read.csv(here("data","PTS-2022.csv"))
head(pts)

#prepare data to merge

pts$SupNum_COW <- pts$COW_Code_N
pts$year <- pts$Year

pts <- pts[6:16]

# create a new dataframe with all other data plus pts data

pts_full_data <- left_join(full_data,pts, by = c("SupNum_COW","year"))
pts_full_data <- pts_full_data[which(pts_full_data$year >= 1976),]



# create dataframe with just non-democractic supporter states
# 

pts_autocracies <- pts_full_data[which(pts_full_data$supp_autocratic == 1),]

autocracies_data <- full_data[which(full_data$supp_autocratic == 1),]


```

## Descriptive data

### Summary Statistics


```{r echo=FALSE, comment = ""}

# ratio of opposition size measure to W measure (both normalized)
# 
cat("ratio of opposition size measure to W measure (both normalized)")
summary(full_data$opp_W_ratio)

# ratio of support group size measure to W measure (both normalized)
summary(full_data$supp_W_ratio)

# ratio of opposition group size measure to support group size measure to W measure (both normalized)
summary(full_data$opp_supp_ratio)

# supporter is democratic (binary)
summary(full_data$supp_democratic)

#target is democratic (binary)
summary(full_data$targ_democratic)

#normalized measure of W based on Smith and Bueno de Mesquita 2022
summary(full_data$W_norm)

## Autocracy binary in full data (mean is proportion)
## 
summary(full_data$supp_autocratic)

summary(autocracies_data$Num_S_TrainCamp)


```

### Plots

```{r echo=FALSE}

hist(full_data$opp_supp_ratio, main = "Histogram of \n Opposition to support ratio")

hist(full_data$Num_S_TrainCamp, main = "Histogram of Number of groups \n supported with training camps \n all regime types")

hist(autocracies_data$Num_S_TrainCamp, main = "Histogram of Number of groups \n supported with training camps \n autocracies only")


```


## Hypotheses

                + H1 Regimes with higher levels of opposition are more likely to support NAGS, all else equal
                + H2 Regimes with higher levels of opposition are more likely to support NAGS that target democracies, all else equal
                + H3 Regimes with lower levels of military capability are more likely to support NAGS, all else equal
                + H4 Regimes with lower levels of millitary capability are more likely to support NAGs that target democracies, all else equal
                + H5 If regimes substitute NAGS for repression, regimes with lower levels of repression are more likely to support NAGS, all else equal.
                + H6 If signals are successful, regimes with higher support for NAGS will have lower levels of protest 
        
                
## Models

### Issues

                + Zero-inflation
                + overdispersion
                
### Poisson, quasipoisson, and hurdle models for legitimating ideology               
                
```{r echo=FALSE}
library(MASS)
library(pscl)


## model on legitimation by ideology autocracies only
## 


model_ideo <- glm(NumNAG_S ~ v2exl_legitideol, family  = poisson(link = "log"), data = autocracies_data)
summary(model_ideo)
exp(coef(model_ideo))

model_ideo_qp <- glm(NumNAG_S ~ v2exl_legitideol, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(model_ideo_qp)
exp(coef(model_ideo_qp))


model_ideo_hurdle <- hurdle(NumNAG_S ~ v2exl_legitideol | v2exl_legitideol, data = autocracies_data)
summary(model_ideo_hurdle)

hurdle_part_ideo <- glm(I(NumNAG_S>0) ~ v2exl_legitideol, family  = binomial(link = "logit"), data = autocracies_data)
summary(hurdle_part_ideo)
exp(coef(hurdle_part_ideo))

## Exponentiated coefficients
expCoef <- exp(coef((model_ideo_hurdle)))
expCoef <- matrix(expCoef, ncol = 2)
rownames(expCoef) <- names(coef(hurdle_part_ideo))
colnames(expCoef) <- c("Count_model","Zero_hurdle_model")
expCoef




```

### Models for hypotheses

#### H1 Regimes with higher levels of opposition are more likely to support NAGS, all else equal

```{r echo=FALSE}

formulah1 <- NumNAG_S ~ targ_democratic + oppsize_norm + WarOnTerror + ColdWar + supporter_cinc + target_cinc + capdist

formulah1b <- Num_S_TrainCamp ~ targ_democratic + oppsize_norm + WarOnTerror + ColdWar + supporter_cinc + target_cinc + capdist
        
        
#Poisson model using Number of groups supported

h1_numS <- glm(formula = formulah1, family  = poisson(link = "log"), data = autocracies_data)
summary(h1_numS)
exp(coef(h1_numS))

# quasipoisson model using number of groups supported

h1_numSq <- glm(formula = formulah1, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h1_numSq)
exp(coef(h1_numSq))

# negative binomial model using number of groups supported

h1_numSnb <- glm.nb(formula = formulah1, data = autocracies_data)
summary(h1_numSnb)
exp(coef(h1_numSnb))


# Hurdle model

h1_hurdle <- hurdle(formula = formulah1, data = autocracies_data)
summary(h1_hurdle)

h1_hurdle_part <- glm(I(NumNAG_S>0) ~ targ_democratic + oppsize_norm + WarOnTerror + ColdWar + supporter_cinc + target_cinc + capdist, family  = binomial(link = "logit"), data = autocracies_data)
summary(h1_hurdle_part)
exp(coef(h1_hurdle_part))

## Exponentiated coefficients
expCoefh1 <- exp(coef((h1_hurdle)))
expCoefh1 <- matrix(expCoefh1, ncol = 2)
rownames(expCoefh1) <- names(coef(h1_hurdle_part))
colnames(expCoefh1) <- c("Count_model","Zero_hurdle_model")
expCoefh1

#Model using number of groups with training camps in country
#

#Poisson model using Number of groups with training camps in country

h1_numSb <- glm(formula = formulah1b, family  = poisson(link = "log"), data = autocracies_data)
summary(h1_numSb)
exp(coef(h1_numSb))

# quasipoisson model using number of groups supported

h1_numSqb <- glm(formula = formulah1b, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h1_numSqb)
exp(coef(h1_numSqb))

# negative binomial model using number of groups supported

h1_numSnbb <- glm.nb(formula = formulah1b, data = autocracies_data)
summary(h1_numSnbb)
exp(coef(h1_numSnbb))


# Hurdle model

h1_hurdleb <- hurdle(formula = formulah1b, data = autocracies_data)
summary(h1_hurdleb)

h1_hurdle_partb <- glm(I(Num_S_TrainCamp>0) ~ targ_democratic + oppsize_norm + WarOnTerror + ColdWar + supporter_cinc + target_cinc + capdist, family  = binomial(link = "logit"), data = autocracies_data)
summary(h1_hurdle_partb)
exp(coef(h1_hurdle_partb))

## Exponentiated coefficients
expCoefh1b <- round(exp(coef((h1_hurdleb))), digits = 5)
expCoefh1b <- matrix(expCoefh1b, ncol = 2)
rownames(expCoefh1b) <- names(coef(h1_hurdle_partb))
colnames(expCoefh1b) <- c("Count_model","Zero_hurdle_model")
expCoefh1b

```
#### H2: Regimes with higher levels of opposition are more likely to support NAGS that target democracies, all else equal

```{r echo=FALSE}

formulah2 <- NumNAG_S ~ targ_democratic * oppsize_norm + WarOnTerror + ColdWar + supporter_cinc + target_cinc + capdist

formulah2b <- Num_S_TrainCamp ~ targ_democratic * oppsize_norm + WarOnTerror + ColdWar + supporter_cinc + target_cinc + capdist

#Poisson model using Number of groups supported

h2_numS <- glm(formula = formulah2, family  = poisson(link = "log"), data = autocracies_data)
summary(h2_numS)
exp(coef(h2_numS))

# quasipoisson model using number of groups supported

h2_numSq <- glm(formula = formulah2, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h2_numSq)
exp(coef(h2_numSq))

# negative binomial model using number of groups supported

h2_numSnb <- glm.nb(formula = formulah2, data = autocracies_data)
summary(h2_numSnb)
exp(coef(h2_numSnb))


# Hurdle model

h2_hurdle <- hurdle(formula = formulah2, data = autocracies_data)
summary(h2_hurdle)

h2_hurdle_part <- glm(I(NumNAG_S>0) ~ targ_democratic * oppsize_norm + WarOnTerror + ColdWar + supporter_cinc + target_cinc + capdist, family  = binomial(link = "logit"), data = autocracies_data)
summary(h2_hurdle_part)
exp(coef(h2_hurdle_part))

## Exponentiated coefficients
expCoefh2 <- exp(coef((h2_hurdle)))
expCoefh2 <- matrix(expCoefh2, ncol = 2)
rownames(expCoefh2) <- names(coef(h2_hurdle_part))
colnames(expCoefh2) <- c("Count_model","Zero_hurdle_model")
expCoefh2


#Model using number of groups with training camps in country
#

#Poisson model using Number of groups with training camps in country

h2_numSb <- glm(formula = formulah2b, family  = poisson(link = "log"), data = autocracies_data)
summary(h2_numSb)
exp(coef(h2_numSb))

# quasipoisson model using number of groups supported

h2_numSqb <- glm(formula = formulah2b, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h2_numSqb)
exp(coef(h2_numSqb))

# negative binomial model using number of groups supported

h2_numSnbb <- glm.nb(formula = formulah2b, data = autocracies_data)
summary(h2_numSnbb)
exp(coef(h2_numSnbb))


# Hurdle model

h2_hurdleb <- hurdle(formula = formulah2b, data = autocracies_data)
summary(h2_hurdleb)

h2_hurdle_partb <- glm(I(Num_S_TrainCamp>0) ~ targ_democratic * oppsize_norm + WarOnTerror + ColdWar + supporter_cinc + target_cinc + capdist, family  = binomial(link = "logit"), data = autocracies_data)
summary(h2_hurdle_partb)
exp(coef(h2_hurdle_partb))

## Exponentiated coefficients
expCoefh2b <- round(exp(coef((h2_hurdleb))), digits = 5)
expCoefh2b <- matrix(expCoefh2b, ncol = 2)
rownames(expCoefh2b) <- names(coef(h2_hurdle_partb))
colnames(expCoefh2b) <- c("Count_model","Zero_hurdle_model")
expCoefh2b

```


#### H3 Regimes with lower levels of military capability are more likely to support NAGS, all else equal

#### H4 Regimes with lower levels of millitary capability are more likely to support NAGs that target democracies, all else equal
             
#### H5 If regimes substitute NAGS for repression, regimes with lower levels of repression are more likely to support NAGS, all else equal.
             
#### H6 If signals are successful, regimes with higher support for NAGS will have lower levels of protest 




```{r echo=FALSE}


library(MASS)
library(pscl)


## model on legitimation by ideology autocracies only
## 


model_ideo <- glm(NumNAG_S ~ v2exl_legitideol, family  = poisson(link = "log"), data = autocracies_data)
summary(model_ideo)
exp(coef(model_ideo))

model_ideo_qp <- glm(NumNAG_S ~ v2exl_legitideol, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(model_ideo_qp)
exp(coef(model_ideo_qp))


model_ideo_hurdle <- hurdle(NumNAG_S ~ v2exl_legitideol | v2exl_legitideol, data = autocracies_data)
summary(model_ideo_hurdle)


## model on full data with just target democracy variable
## 

model_base <- glm.nb(NumNAG_S ~ targ_democratic, data = full_data)
summary(model_base)

# model base with control for time period variables

model_basec <- glm.nb(NumNAG_S ~ targ_democratic + WarOnTerror + ColdWar, data = full_data)
summary(model_basec)

## model base with supporter democratic or non-democratic

model_based <- glm.nb(NumNAG_S ~ targ_democratic + supp_democratic + WarOnTerror + ColdWar, data = full_data)
summary(model_based)

# models with just opposition and support group sizes
# 

model_opposition <- glm.nb(NumNAG_S ~ targ_democratic + oppsize_norm + WarOnTerror + ColdWar, data = autocracies_data)
summary(model_opposition)

model_oppositionTrainCamp <- glm.nb(Num_S_TrainCamp ~ targ_democratic + oppsize_norm + WarOnTerror + ColdWar, data = autocracies_data)
summary(model_oppositionTrainCamp)


model_support <- glm.nb(NumNAG_S ~ targ_democratic + suppsize_norm +  WarOnTerror + ColdWar, data = autocracies_data)
summary(model_support)

model_supportTrainCamp <- glm.nb(Num_S_TrainCamp ~ targ_democratic + suppsize_norm + WarOnTerror + ColdWar, data = autocracies_data)
summary(model_supportTrainCamp)
        


## Model W - just the effect of W
## 


modelWTrainCamp <- glm.nb(Num_S_TrainCamp ~ targ_democratic + W_norm + WarOnTerror + ColdWar, data = autocracies_data)
summary(modelWTrainCamp)

#ratio of actual support to W - how close are they to a truly minimal winning coalition
#
model1TrainCamp <- glm.nb(Num_S_TrainCamp ~ targ_democratic + supp_W_ratio + WarOnTerror + ColdWar, data = autocracies_data)
summary(model1TrainCamp)


# ratio of opponent size to W - how close are the opposition to having a minimal winning coalition of their own

model2TrainCamp <-  glm.nb(Num_S_TrainCamp ~ targ_democratic + opp_W_ratio + WarOnTerror + ColdWar, data = autocracies_data)
summary(model2TrainCamp)



# ratio of opposition to supporters - head to head match up
# 

model3TrainCamp <- glm.nb(Num_S_TrainCamp ~ targ_democratic + opp_supp_ratio + WarOnTerror + ColdWar, data = autocracies_data)
summary(model3TrainCamp)


## multivariate model - ideology, opp_supp_ratio, strategic variables
##  v2exl_legitideol

modelmulti_traincamp <- glm.nb(Num_S_TrainCamp ~ targ_democratic + opp_supp_ratio + v2exl_legitideol + WarOnTerror + ColdWar + supporter_milex + target_milex, data = autocracies_data)
summary(modelmulti_traincamp)

modelmulti_traincamp2 <- glm.nb(Num_S_TrainCamp ~ targ_democratic + opp_supp_ratio + v2exl_legitideol + WarOnTerror + ColdWar + supporter_cinc + target_cinc, data = autocracies_data)
summary(modelmulti_traincamp2)



```

## Model Plots and Predictions

```{r echo=FALSE}



```


