---
title: "Data Loading, Cleaning, and Organization"
format: html
---


```{r echo = FALSE}

options(scipen=999)

#Loading NAGS dyadic (supporter-target) data

library(here)
library(readr)
nags_data1 <- read_delim(here("data","Dyadic_Target-Supporter_active_support.csv"), delim = ";", escape_double = FALSE, trim_ws = TRUE)


nags_data1 <- nags_data1[which(nags_data1$Year > 1945),]

nags_data1$year <- nags_data1$Year
nags_data1$COWcode <- nags_data1$SupNum_COW

head(nags_data1)

```

```{r echo=FALSE}

# creating polity scores for supporter and target countries

#load polity data set for suppoters
#
library(readxl)
support_polity <- read_excel("data/p5v2018.xls")
head(support_polity)

#create score labels for supporters
support_polity$supporter_p5 <- support_polity$p5
support_polity$supporter_cyear <- support_polity$cyear
support_polity$supporter_flag <- support_polity$flag
support_polity$SupNum_COW <- support_polity$ccode 
support_polity$supporter_democ <- support_polity$democ 
support_polity$supporter_autoc <- support_polity$autoc
support_polity$supporter_polity <- support_polity$polity
support_polity$supporter_polity2 <- support_polity$polity2
support_polity$supporter_durable <- support_polity$durable

#select only the supporter named variables

support_polity <- support_polity[c(6,38:46)]

#repeat the above for target countries

#load polity data set for targets
#
target_polity <- read_excel("data/p5v2018.xls")
head(target_polity)

#create score labels for targets
target_polity$target_p5 <- target_polity$p5
target_polity$target_cyear <- target_polity$cyear
target_polity$target_flag <- target_polity$flag
target_polity$TarNum_COW <- target_polity$ccode 
target_polity$target_democ <- target_polity$democ 
target_polity$target_autoc <- target_polity$autoc
target_polity$target_polity <- target_polity$polity
target_polity$target_polity2 <- target_polity$polity2
target_polity$target_durable <- target_polity$durable

#select only the target named variables

target_polity <- target_polity[c(6,38:46)]


```

```{r echo=FALSE}
# Merge polity data for supporters
library(dplyr)
nags_data1 <- left_join(nags_data1,support_polity, by = c("SupNum_COW","year"))

# Merge polity data for targets

nags_data1 <- left_join(nags_data1,target_polity, by = c("TarNum_COW","year"))

# add national capabilities data for supporters and targets

# load national material capabilities data
# 

NMC<- read_csv(here("data","NMC-60-abridged.csv"))
head(NMC)

NMC$COWcode <- NMC$ccode

NMC <- NMC[which(NMC$year > 1945 & NMC$year < 2011),]

NMC <- NMC[c(3:12)]

NMC_supp <- NMC

NMC_supp$SupNum_COW <- NMC_supp$COWcode
NMC_supp$supporter_milex <- NMC_supp$milex
NMC_supp$supporter_milper <- NMC_supp$milper
NMC_supp$supporter_irst <- NMC_supp$irst
NMC_supp$supporter_pec <- NMC_supp$pec
NMC_supp$supporter_tpop <- NMC_supp$tpop
NMC_supp$supporter_upop <- NMC_supp$upop
NMC_supp$supporter_cinc <- NMC_supp$cinc

NMC_supp <- NMC_supp[c(1,11:18)]

NMC_targ <- NMC

NMC_targ$TarNum_COW <- NMC_targ$COWcode
NMC_targ$target_milex <- NMC_targ$milex
NMC_targ$target_milper <- NMC_targ$milper
NMC_targ$target_irst <- NMC_targ$irst
NMC_targ$target_pec <- NMC_targ$pec
NMC_targ$target_tpop <- NMC_targ$tpop
NMC_targ$target_upop <- NMC_targ$upop
NMC_targ$target_cinc <- NMC_targ$cinc

NMC_targ <- NMC_targ[c(1,11:18)]

nags_data1 <- left_join(nags_data1,NMC_supp, by = c("SupNum_COW","year"))

nags_data1 <- left_join(nags_data1,NMC_targ, by = c("TarNum_COW","year"))


```



```{r echo=FALSE}

countries_data <- read_csv(here("data","vdem_plus_w.csv"))
head(countries_data)

countries_data <- countries_data[which(countries_data$year < 2011),]

library(dplyr)

full_data <- left_join(nags_data1,countries_data, by = c("COWcode","year"))

# vdem_select1 <- vdem_w_select[which(vdem_w_select$year > 1945),]




```


## To Do (variables)

                + Use Cshapes to add minimum distance between states in dyad - done
                + Use Cshapes to add distance between capitals in dyad - done
                + Add variable for violent repression (PTS data has limitations - only post-1976 and includes all state violence not just political repression)
                + State capacity
                
## Additional Sources

                + For protests, riots, and violence against civilians)
                (https://acleddata.com/data-export-tool/
                + For general levels of poltical terror - Political Terror Scale


```{r echo=FALSE}
# summary(full_data$W_norm)

# create a democracy target variable
# 


full_data$targ_democratic <- ifelse(full_data$target_polity > 6,1,0)
# summary(full_data$targ_democratic)

#create a binary democracy variable for supporters 

full_data$supp_democratic <- ifelse(full_data$supporter_polity > 6,1,0)
# summary(full_data$supp_democratic)




# normalize opposition and support group size variables
# 


minopp <- min(full_data$v2regoppgroupssize, na.rm = TRUE)
maxopp <- max(full_data$v2regoppgroupssize, na.rm = TRUE)


full_data$oppsize_norm <- (full_data$v2regoppgroupssize - minopp ) / (maxopp - minopp)


minsupp <- min(full_data$v2regsupgroupssize, na.rm = TRUE)
maxsupp <- max(full_data$v2regsupgroupssize, na.rm = TRUE)

full_data$suppsize_norm <- (full_data$v2regsupgroupssize - minsupp) / (maxsupp - minsupp)


summary(full_data$suppsize_norm)
summary(full_data$oppsize_norm)



# create a variable of ratio of opposition to support group size

full_data$opp_supp_ratio <- full_data$oppsize_norm / full_data$suppsize_norm
# summary(full_data$opp_supp_ratio)

# create variable of ratio of support size score to W score
# 

full_data$supp_W_ratio <- full_data$suppsize_norm / full_data$W_norm
# summary(full_data$supp_W_ratio)


# create variable of ratio of opposition to W

full_data$opp_W_ratio <- full_data$oppsize_norm / full_data$W_norm
# summary(full_data$opp_W_ratio)


# create variables for Cold War and War on Terror (post-911)

full_data$ColdWar <- ifelse(full_data$year < 1991,1,0)
# summary(full_data$ColdWar)

full_data$WarOnTerror <- ifelse(full_data$year > 2001,1,0)
# summary(full_data$WarOnTerror)


## use cshapes data to include minimum distance and distance between capitals
## 

library(cshapes)

#create a vector of dates for years in data set

cap_dist <- distlist(date = as.Date("2010-01-01"), type = "capdist", useGW = FALSE)

cap_dist$SupNum_COW <- cap_dist$ccode1
cap_dist$TarNum_COW <- cap_dist$ccode2
cap_dist <- cap_dist[c(3:5)]

# min_dist <- distlist(date = as.Date("2010-01-01"), type = "mindist", useGW = FALSE)
# 
# min_dist$SupNum_COW <- min_dist$ccode1
# min_dist$TarNum_COW <- min_dist$ccode2
# min_dist <- min_dist[c(3:5)]
# 
# write.csv(min_dist, file = here("data","min_dist.csv"))
# 

min_dist <- read_csv(here("data","min_dist.csv"))
min_dist <- min_dist[c(2:4)]

full_data <- left_join(full_data,cap_dist, by = c("SupNum_COW","TarNum_COW"))

full_data <- left_join(full_data,min_dist, by = c("SupNum_COW","TarNum_COW"))


# retrieve state capacity data
# 

library(haven)
state_cap <- read_dta(here("data","StateCapacityDataset_v1.dta"))
View(state_cap)

state_cap$SupNum_COW <- state_cap$ccode
state_cap$capacity <- state_cap$Capacity

minmilexpercap <- min(state_cap$milexpercap, na.rm = TRUE)
maxmilexpercap <- max(state_cap$milexpercap, na.rm = TRUE)

state_cap$milex_percap_norm <- (state_cap$milexpercap - minmilexpercap) / (maxmilexpercap - minmilexpercap)


minmilpercap <- min(state_cap$milpercap, na.rm = TRUE)
maxmilpercap <- max(state_cap$milpercap, na.rm = TRUE)

state_cap$milpercap_norm <- (state_cap$milpercap - minmilpercap) / (maxmilpercap - minmilpercap)

state_cap <- state_cap[c(3,34:37)]

full_data <- left_join(full_data,state_cap, by = c("SupNum_COW","year"))

#create binary variable for autocracy (used later to create subsets)
full_data$supp_autocratic <- ifelse(full_data$supporter_polity < -5,1,0)

full_data$supp_autocratic2 <- ifelse(full_data$v2x_regime_amb < 4,1,0)



# # Political Terror Scale data
# # 
# 
# pts <- read.csv(here("data","PTS-2022.csv"))
# head(pts)

# #prepare data to merge
# 
# pts$SupNum_COW <- pts$COW_Code_N
# pts$year <- pts$Year

# pts <- pts[6:16]

# create a new dataframe with all other data plus pts data

# pts_full_data <- left_join(full_data,pts, by = c("SupNum_COW","year"))
# pts_full_data <- pts_full_data[which(pts_full_data$year >= 1976),]
# 


# create dataframe with just non-democractic supporter states
# 

# pts_autocracies <- pts_full_data[which(pts_full_data$supp_autocratic == 1),]

autocracies_data <- full_data[which(full_data$supp_autocratic == 1),]

autocracies_data_v <- full_data[which(full_data$supp_autocratic2 == 1),]


write.csv(full_data, here("data","full_data.csv"))

write.csv(autocracies_data, here("data","autocracies_data.csv"))

write.csv(autocracies_data_v, here("data","autocracies_data_v.csv"))


```

