---
title: "Support for non-state armed groups as domestic signaling in autocracies"
output:
  html_document:
    df_print: paged
editor_options: 
  chunk_output_type: console
---

## Data Load

```{r echo=FALSE}
options(scipen = 999)
library(stargazer)
library(here)

autocracies_data <- read.csv(here("data","autocracies_data_v.csv"))

autocracies_data$NAGs_Supported <- autocracies_data$NumNAG_S
autocracies_data$NAGS_with_Training_Camps <- autocracies_data$Num_S_TrainCamp
autocracies_data$opposition_size <- autocracies_data$oppsize_norm
autocracies_data$W <- autocracies_data$W_norm
autocracies_data$distance_between_capitals <- autocracies_data$capdist


hurdle_count_n <- autocracies_data[which(autocracies_data$NumNAG_S > 0),]

hurdle_count_t <- autocracies_data[which(autocracies_data$Num_S_TrainCamp >0),]



```




```{r echo=FALSE, comment = ""}

#normalized measure of W based on Smith and Bueno de Mesquita 2022
summary(autocracies_data$W)

#normalized measure of opposition size
summary(autocracies_data$opposition_size)


#Number of NAGS with training camps hosted in supporting country
summary(autocracies_data$NAGS_with_Training_Camps)

#Number of NAGS actively supported
summary(autocracies_data$NAGs_Supported)


# ratio of opposition size measure to W measure (both normalized)
# 
cat("ratio of opposition size measure to W measure (both normalized)")
summary(autocracies_data$opp_W_ratio)

# ratio of support group size measure to W measure (both normalized)
summary(autocracies_data$supp_W_ratio)

# ratio of opposition group size measure to support group size measure to W measure (both normalized)
summary(autocracies_data$opp_supp_ratio)

# supporter is democratic (binary)
summary(autocracies_data$supp_democratic)

#target is democratic (binary)
summary(autocracies_data$targ_democratic)

```

## Summary Plots

```{r echo=FALSE}

hist(autocracies_data$NAGs_Supported, main = "Histogram of Number of groups \n actively supported \n autocracies only")

hist(autocracies_data$NAGS_with_Training_Camps, main = "Histogram of Number of groups \n supported with training camps \n autocracies only")

hist(autocracies_data$opposition_size, main = "Histogram of \n Opposition Size")

hist(autocracies_data$W, main = "Histogram of \n Minimal Winning Coalition Size (W)")



```

Models:

- HW: Autocratic regimes with smaller W and ideological support groups will be more likely to support NAGS, all else equal. (Smaller W predicts greater use of private payoffs to maintain W. I argue that ideological payoffs substitute for private payoffs.)




```{r echo=FALSE}
library(MASS)
library(pscl)
library(VGAM)


formulaw1 <- NAGs_Supported ~ W *  v2exl_legitideol + WarOnTerror + ColdWar + distance_between_capitals  

formulaw1b <- NAGS_with_Training_Camps ~ W * v2exl_legitideol +  WarOnTerror + ColdWar + distance_between_capitals  


# quasipoisson model using number of groups supported

w1_numSq <- glm(formula = formulaw1, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(w1_numSq)
exp(coef(w1_numSq))


# Hurdle model

w1_hurdle <- hurdle(formula = formulaw1, data = autocracies_data)
summary(w1_hurdle)

w1_hurdle_part <- glm(I(NAGs_Supported>0) ~ W * v2exl_legitideol +  WarOnTerror + ColdWar + distance_between_capitals , family  = binomial(link = "logit"), data = autocracies_data)
summary(w1_hurdle_part)
exp(coef(w1_hurdle_part))



w1_count_part <- vglm(formula = formulaw1, family  = pospoisson(), data = hurdle_count_n)
summary(w1_count_part)



#Model using number of groups with training camps in country
#

# quasipoisson model using number of groups supported

w1_numSqb <- glm(formula = formulaw1b, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(w1_numSqb)
exp(coef(w1_numSqb))


# Hurdle model

w1_hurdleb <- hurdle(formula = formulaw1b, data = autocracies_data)
summary(w1_hurdleb)

w1_hurdle_partb <- glm(I(NAGS_with_Training_Camps>0) ~ W * v2exl_legitideol + WarOnTerror + ColdWar + distance_between_capitals , family  = binomial(link = "logit"), data = autocracies_data)
summary(w1_hurdle_partb)
exp(coef(w1_hurdle_partb))

w1_count_part <- vglm(formula = formulaw1, family  = pospoisson(), data = hurdle_count_n)
summary(w1_count_part)

cat("\n w1_hurdle - number supported \n")

## Exponentiated coefficients
expCoefw1 <- exp(coef((w1_hurdle)))
expCoefw1 <- matrix(expCoefw1, ncol = 2)
rownames(expCoefw1) <- names(coef(w1_hurdle_part))
colnames(expCoefw1) <- c("Count_model","Zero_hurdle_model")
expCoefw1

cat("\n w1_hurdle - number with training camps \n")

## Exponentiated coefficients
expCoefw1b <- round(exp(coef((w1_hurdleb))), digits = 5)
expCoefw1b <- matrix(expCoefw1b, ncol = 2)
rownames(expCoefw1b) <- names(coef(w1_hurdle_partb))
colnames(expCoefw1b) <- c("Count_model","Zero_hurdle_model")
expCoefw1b

# library(stargazer)
# stargazer(w1_hurdle_part)
# stargazer(w1_hurdle_partb)
# 
# stargazer(w1_numSq)
# stargazer(w1_numSqb)

```


H1: Autocratic regimes with larger opposition groups will be more likely to actively support NAGs, all else equal.

```{r}

formulah1 <- NAGs_Supported ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals  + W


h1_hurdle_part <- glm(I(NAGs_Supported>0) ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals, family  = binomial(link = "logit"), data = autocracies_data)
summary(h1_hurdle_part)
exp(coef(h1_hurdle_part))


```


H2: Autocratic regimes with larger opposition groups will be more likely to actively support NAGs by hosting training camps, all else equal. 


```{r}



formulah2 <- NAGS_with_Training_Camps ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals  + W + NAGs_Supported


h2_hurdle_part <- glm(I(NAGS_with_Training_Camps>0) ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals  + W + NAGs_Supported, family  = binomial(link = "logit"), data = autocracies_data)
summary(h2_hurdle_part)
exp(coef(h2_hurdle_part))


```


H3: Autocratic regimes with larger opposition groups and pro-democracy civil society movements will be more likely to actively support NAGS that target democracies by hosting training camps, all else equal. 

```{r}

h3_hurdle_part <- glm(I(NAGS_with_Training_Camps>0 & targ_democratic == 1) ~ opposition_size *  v2csanmvch_4 + WarOnTerror + ColdWar + distance_between_capitals + v2x_regime_amb, family  = binomial(link = "logit"), data = autocracies_data)
summary(h3_hurdle_part)
exp(coef(h3_hurdle_part))



```

H4: Instrumental variable using 2S IV Regression with a linear probability model
