---
title: "Support for non-state armed groups as domestic signaling in autocracies"
output:
  html_document:
    df_print: paged
editor_options: 
  chunk_output_type: console
---

## Data Load

```{r echo=FALSE}
options(scipen = 999)
library(stargazer)
library(here)

autocracies_data <- read.csv(here("data","autocracies_data.csv"))

autocracies_data$NAGs_Supported <- autocracies_data$NumNAG_S
autocracies_data$NAGS_with_Training_Camps <- autocracies_data$Num_S_TrainCamp
autocracies_data$opposition_size <- autocracies_data$oppsize_norm
autocracies_data$W <- autocracies_data$W_norm
autocracies_data$distance_between_capitals <- autocracies_data$capdist

autocracies_data$nags_1_plus <- ifelse(autocracies_data$NAGs_Supported > 0,1,0)

autocracies_data$camps_1_plus <- ifelse(autocracies_data$NAGS_with_Training_Camps>0,1,0)


hurdle_count_n <- autocracies_data[which(autocracies_data$NumNAG_S > 0),]

hurdle_count_t <- autocracies_data[which(autocracies_data$Num_S_TrainCamp >0),]



#Need to create a dyad code, so I can make it dyad-year unit of observation

autocracies_data$dyad <- paste(autocracies_data$SupNum_COW,autocracies_data$TarNum_COW,sep='-')

autocracies_data$dyad <- as.factor(autocracies_data$dyad)

library(plm)
library(pglm)

autocracies_data <- pdata.frame(autocracies_data, index = c("dyad","year"))

View(table(index(autocracies_data), useNA = "ifany"))

```




```{r echo=FALSE, comment = ""}

#target regime types
summary(autocracies_data$targ_democratic)

#normalized measure of W based on Smith and Bueno de Mesquita 2022
summary(autocracies_data$W)

#normalized measure of opposition size
summary(autocracies_data$opposition_size)

#Number of NAGS with training camps hosted in supporting country
summary(autocracies_data$NAGS_with_Training_Camps)

#Number of NAGS actively supported
summary(autocracies_data$NAGs_Supported)

# ratio of opposition size measure to W measure (both normalized)
# 
cat("ratio of opposition size measure to W measure (both normalized)")
summary(autocracies_data$opp_W_ratio)

# ratio of support group size measure to W measure (both normalized)
summary(autocracies_data$supp_W_ratio)

# ratio of opposition group size measure to support group size measure to W measure (both normalized)
summary(autocracies_data$opp_supp_ratio)

# supporter is democratic (binary)
summary(autocracies_data$supp_democratic)

#target is democratic (binary)
summary(autocracies_data$targ_democratic)

```

## Summary Plots

```{r echo=FALSE}

hist(autocracies_data$NAGs_Supported, main = "Histogram of Number of groups \n actively supported \n autocracies only")

hist(autocracies_data$NAGS_with_Training_Camps, main = "Histogram of Number of groups \n supported with training camps \n autocracies only")

hist(autocracies_data$opposition_size, main = "Histogram of \n Opposition Size")

hist(autocracies_data$W, main = "Histogram of \n Minimal Winning Coalition Size (W)")



```

Models:

- HW: Autocratic regimes with smaller W and ideological support groups will be more likely to support NAGS, all else equal. (Smaller W predicts greater use of private payoffs to maintain W. I argue that ideological payoffs substitute for private payoffs.)




```{r echo=FALSE}
library(MASS)
library(pscl)
library(VGAM)
library(survival)
library(bife)


formulaw1 <- NAGs_Supported ~ W *  v2exl_legitideol + WarOnTerror + ColdWar + distance_between_capitals  

formulaw1b <- NAGS_with_Training_Camps ~ W * v2exl_legitideol +  WarOnTerror + ColdWar + distance_between_capitals  


# quasipoisson model using number of groups supported

w1_numSq <- glm(formula = formulaw1, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(w1_numSq)
exp(coef(w1_numSq))


# Hurdle model

w1_hurdle <- hurdle(formula = formulaw1, data = autocracies_data)
summary(w1_hurdle)

w1_hurdle_part <- w1_hurdle_part <- glm(I(NAGs_Supported>0) ~ W * v2exl_legitideol +  WarOnTerror + ColdWar, family  = binomial(link = "logit"), data = autocracies_data)
summary(w1_hurdle_part)
exp(coef(w1_hurdle_part))

w1_partp <- plm(nags_1_plus ~ W * v2exl_legitideol +  WarOnTerror + ColdWar, data = autocracies_data, effect = "twoways", model = "within")
summary(w1_partp)
exp(coef(w1_partp))

w1_hurdle_partb <- bife(I(NAGs_Supported>0) ~ W * v2exl_legitideol +  WarOnTerror + ColdWar | dyad , model = "logit", data = autocracies_data)
summary(w1_hurdle_partb)
exp(coef(w1_hurdle_partb))


w1_count_part <- vglm(formula = formulaw1, family  = pospoisson(), data = hurdle_count_n)
summary(w1_count_part)



#Model using number of groups with training camps in country
#

# quasipoisson model using number of groups supported

w1_numSqb <- glm(formula = formulaw1b, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(w1_numSqb)
exp(coef(w1_numSqb))


# Hurdle model

w1_hurdleb <- hurdle(formula = formulaw1b, data = autocracies_data)
summary(w1_hurdleb)

w1_hurdle_partb <- glm(I(NAGS_with_Training_Camps>0) ~ W * v2exl_legitideol + WarOnTerror + ColdWar + distance_between_capitals , family  = binomial(link = "logit"), data = autocracies_data)
summary(w1_hurdle_partb)
exp(coef(w1_hurdle_partb))

w1_count_part <- vglm(formula = formulaw1, family  = pospoisson(), data = hurdle_count_n)
summary(w1_count_part)

cat("\n w1_hurdle - number supported \n")

## Exponentiated coefficients
expCoefw1 <- exp(coef((w1_hurdle)))
expCoefw1 <- matrix(expCoefw1, ncol = 2)
rownames(expCoefw1) <- names(coef(w1_hurdle_part))
colnames(expCoefw1) <- c("Count_model","Zero_hurdle_model")
expCoefw1

cat("\n w1_hurdle - number with training camps \n")

## Exponentiated coefficients
expCoefw1b <- round(exp(coef((w1_hurdleb))), digits = 5)
expCoefw1b <- matrix(expCoefw1b, ncol = 2)
rownames(expCoefw1b) <- names(coef(w1_hurdle_partb))
colnames(expCoefw1b) <- c("Count_model","Zero_hurdle_model")
expCoefw1b

# library(stargazer)
# stargazer(w1_hurdle_part)
# stargazer(w1_hurdle_partb)
# 
# stargazer(w1_numSq)
# stargazer(w1_numSqb)

```


H1: Autocratic regimes with larger opposition groups will be more likely to actively support NAGs, all else equal.

```{r}

formulah1 <- NAGs_Supported ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals  + W


h1_hurdle_part <- glm(I(NAGs_Supported>0) ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals, family  = binomial(link = "logit"), data = autocracies_data)
summary(h1_hurdle_part)
exp(coef(h1_hurdle_part))

h1_partp <- plm(nags_1_plus ~ opposition_size + WarOnTerror + ColdWar, data = autocracies_data, effect = "twoways", model = "within")
summary(h1_partp)
exp(coef(h1_partp))


```


H2: Autocratic regimes with larger opposition groups will be more likely to actively support NAGs by hosting training camps, all else equal. 


```{r}



formulah2 <- NAGS_with_Training_Camps ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals 


h2_hurdle_part <- glm(camps_1_plus ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals, family  = binomial(link = "logit"), data = autocracies_data)
summary(h2_hurdle_part)
exp(coef(h2_hurdle_part))

h2_partl <- lm(camps_1_plus ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals, data = autocracies_data)
summary(h2_partl)

h2_partp <- plm(camps_1_plus ~ opposition_size + WarOnTerror + ColdWar, data = autocracies_data, effect = "individual", model = "within")
summary(h2_partp)



```


H3: Autocratic regimes with larger opposition groups will be more likely to actively support NAGS that target democracies by hosting training camps, all else equal. 

```{r}

h3_hurdle_part <- glm(I(NAGS_with_Training_Camps>0 & targ_democratic == 1) ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals + v2x_regime_amb, family  = binomial(link = "logit"), data = autocracies_data)
summary(h3_hurdle_part)
exp(coef(h3_hurdle_part))



```



H4: Autocratic regimes with larger opposition groups and pro-democracy civil society movements will be more likely to actively support NAGS that target democracies by hosting training camps, all else equal. 

```{r}

h4_hurdle_part <- glm(I(NAGS_with_Training_Camps>0 & targ_democratic == 1) ~ opposition_size *  v2csanmvch_4 + WarOnTerror + ColdWar + distance_between_capitals + v2x_regime_amb, family  = binomial(link = "logit"), data = autocracies_data)
summary(h4_hurdle_part)
exp(coef(h4_hurdle_part))



```

H5: Large anti-system movements - v2csantimv

```{r}

h5_hurdle_part <- glm(I(NAGS_with_Training_Camps>0 & targ_democratic == 1) ~ v2csantimv + WarOnTerror + ColdWar + distance_between_capitals + v2x_regime_amb, family  = binomial(link = "logit"), data = autocracies_data)
summary(h5_hurdle_part)
exp(coef(h5_hurdle_part))



```



H6: Autocratic regimes with larger opposition groups  will be more likely to actively support NAGS that target democracies by hosting training camps, all else equal. 

Using Instrumental variable using Two stage least squares (2SLS) Regression with a linear probability model

(“Even with these problems, the linear probability model is useful
and often applied in economics. It usually works well for values
of the independent variables that are near the averages in the
sample.” (p.209, Wooldridge, Jeffrey. Introductory Econometrics: A Modern Approach. 6th ed. Mason, OH: CENGAGE Learning Custom Publishing, 2015. )

```{r}

#h3as LPM

h3_lpm <- lm(I(NAGS_with_Training_Camps>0 & targ_democratic == 1) ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals + v2x_regime_amb, data = autocracies_data)
summary(h3_lpm)

library(ivreg)

h3_iv <- ivreg(I(NAGS_with_Training_Camps>0 & targ_democratic == 1) ~  WarOnTerror + ColdWar + distance_between_capitals + v2x_regime_amb | opposition_size | v2csprtcpt , data = autocracies_data)

summary(h3_iv)

library("modelsummary")
m_list <- list(OLS = h3_lpm, IV = h3_iv)
msummary(m_list)


```

