---
title: "R Notebook"
output:
  html_document:
    df_print: paged
editor_options: 
  chunk_output_type: console
---

## Data Load

```{r echo=FALSE}
options(scipen = 999)
library(stargazer)
library(here)

autocracies_data <- read.csv(here("data","autocracies_data.csv"))

autocracies_data$NAGs_Supported <- autocracies_data$NumNAG_S
autocracies_data$NAGS_with_Training_Camps <- autocracies_data$Num_S_TrainCamp
autocracies_data$opposition_size <- autocracies_data$oppsize_norm
autocracies_data$W <- autocracies_data$W_norm
autocracies_data$distance_between_capitals <- autocracies_data$capdist


hurdle_count_n <- autocracies_data[which(autocracies_data$NumNAG_S > 0),]

hurdle_count_t <- autocracies_data[which(autocracies_data$Num_S_TrainCamp >0),]



```

## Summary Stats



```{r echo=FALSE, comment = ""}

#normalized measure of W based on Smith and Bueno de Mesquita 2022
summary(autocracies_data$W)

#normalized measure of opposition size
summary(autocracies_data$opposition_size)


#Number of NAGS with training camps hosted in supporting country
summary(autocracies_data$NAGS_with_Training_Camps)

#Number of NAGS actively supported
summary(autocracies_data$NAGs_Supported)


# ratio of opposition size measure to W measure (both normalized)
# 
cat("ratio of opposition size measure to W measure (both normalized)")
summary(autocracies_data$opp_W_ratio)

# ratio of support group size measure to W measure (both normalized)
summary(autocracies_data$supp_W_ratio)

# ratio of opposition group size measure to support group size measure to W measure (both normalized)
summary(autocracies_data$opp_supp_ratio)

# supporter is democratic (binary)
summary(autocracies_data$supp_democratic)

#target is democratic (binary)
summary(autocracies_data$targ_democratic)




```

## Summary Plots

```{r echo=FALSE}

hist(autocracies_data$NAGs_Supported, main = "Histogram of Number of groups \n actively supported \n autocracies only")

hist(autocracies_data$NAGS_with_Training_Camps, main = "Histogram of Number of groups \n supported with training camps \n autocracies only")

hist(autocracies_data$opposition_size, main = "Histogram of \n Opposition Size")

hist(autocracies_data$W, main = "Histogram of \n Minimal Winning Coalition Size (W)")



```

## Models

- HW: Autocratic regimes with smaller W will be more likely to support NAGS, all else equal. 

```{r echo=FALSE}
library(MASS)
library(pscl)
library(VGAM)

formulaw1 <- NAGs_Supported ~ W + WarOnTerror + ColdWar + distance_between_capitals  

formulaw1b <- NAGS_with_Training_Camps ~ W + WarOnTerror + ColdWar + distance_between_capitals  


# quasipoisson model using number of groups supported

w1_numSq <- glm(formula = formulaw1, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(w1_numSq)
exp(coef(w1_numSq))


# Hurdle model

w1_hurdle <- hurdle(formula = formulaw1, data = autocracies_data)
summary(w1_hurdle)

w1_hurdle_part <- glm(I(NAGs_Supported>0) ~ W + WarOnTerror + ColdWar + distance_between_capitals , family  = binomial(link = "logit"), data = autocracies_data)
summary(w1_hurdle_part)
exp(coef(w1_hurdle_part))



w1_count_part <- vglm(formula = formulaw1, family  = pospoisson(), data = hurdle_count_n)
summary(w1_count_part)



#Model using number of groups with training camps in country
#

# quasipoisson model using number of groups supported

w1_numSqb <- glm(formula = formulaw1b, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(w1_numSqb)
exp(coef(w1_numSqb))


# Hurdle model

w1_hurdleb <- hurdle(formula = formulaw1b, data = autocracies_data)
summary(w1_hurdleb)

w1_hurdle_partb <- glm(I(NAGS_with_Training_Camps>0) ~ W + WarOnTerror + ColdWar + distance_between_capitals , family  = binomial(link = "logit"), data = autocracies_data)
summary(w1_hurdle_partb)
exp(coef(w1_hurdle_partb))

w1_count_part <- vglm(formula = formulaw1, family  = pospoisson(), data = hurdle_count_n)
summary(w1_count_part)

cat("\n w1_hurdle - number supported \n")

## Exponentiated coefficients
expCoefw1 <- exp(coef((w1_hurdle)))
expCoefw1 <- matrix(expCoefw1, ncol = 2)
rownames(expCoefw1) <- names(coef(w1_hurdle_part))
colnames(expCoefw1) <- c("Count_model","Zero_hurdle_model")
expCoefw1

cat("\n w1_hurdle - number with training camps \n")

## Exponentiated coefficients
expCoefw1b <- round(exp(coef((w1_hurdleb))), digits = 5)
expCoefw1b <- matrix(expCoefw1b, ncol = 2)
rownames(expCoefw1b) <- names(coef(w1_hurdle_partb))
colnames(expCoefw1b) <- c("Count_model","Zero_hurdle_model")
expCoefw1b

# library(stargazer)
# stargazer(w1_hurdle_part)
# stargazer(w1_hurdle_partb)
# 
# stargazer(w1_numSq)
# stargazer(w1_numSqb)

```


- H1: Autocratic regimes with large opposition groups will be more likely to support NAGS, all else equal. 

                + H1a: Higher likelihood of supporting at least one NAG.

                + H1b: Higher number of NAGS supported.
                
```{r echo=FALSE}

formulah1 <- NAGs_Supported ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals  + W


# quasipoisson model using number of groups supported

h1_q <- glm(formula = formulah1, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h1_q)
exp(coef(h1_q))


# Hurdle model

h1_hurdle <- hurdle(formula = formulah1, data = autocracies_data)
summary(h1_hurdle)

h1_hurdle_part <- glm(I(NAGs_Supported>0) ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals  + W, family  = binomial(link = "logit"), data = autocracies_data)
summary(h1_hurdle_part)
exp(coef(h1_hurdle_part))

h1_count_part <- vglm(formula = formulah1, family  = pospoisson(), data = hurdle_count_n)
summary(h1_count_part)


cat("\n h1_hurdle - number supported \n")

## Exponentiated coefficients
expCoefh1 <- exp(coef((h1_hurdle)))
expCoefh1 <- matrix(expCoefh1, ncol = 2)
rownames(expCoefh1) <- names(coef(h1_hurdle_part))
colnames(expCoefh1) <- c("Count_model","Zero_hurdle_model")
expCoefh1

# library(stargazer)
# stargazer(h1_q)
# stargazer(h1_hurdle)


```


- H2: Autocratic regimes with large opposition groups will be more likely to support NAGS by hosting training camps, all else equal. 

                + H2a: Higher likelihood of supporting at least one NAG.

                + H2b: Higher number of NAGS supported.
                
```{r echo=FALSE}



#H2 - Models using number of groups with training camps in country
#

formulah2 <- NAGS_with_Training_Camps ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals  + W + NAGs_Supported



# quasipoisson model using number of groups supported

h2_q <- glm(formula = formulah2, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h2_q)
exp(coef(h2_q))


# Hurdle model

h2_hurdle <- hurdle(formula = formulah2, data = autocracies_data)
summary(h2_hurdle)

h2_hurdle_part <- glm(I(NAGS_with_Training_Camps>0) ~ opposition_size + WarOnTerror + ColdWar + distance_between_capitals  + W + NAGs_Supported, family  = binomial(link = "logit"), data = autocracies_data)
summary(h2_hurdle_part)
exp(coef(h2_hurdle_part))

h2_count_part <- vglm(formula = formulah2, family  = pospoisson(), data = hurdle_count_t)
summary(h2_count_part)



cat("\n h2_hurdle - number with training camps \n")



## Exponentiated coefficients
expCoefh2 <- round(exp(coef((h2_hurdle))), digits = 5)
expCoefh2 <- matrix(expCoefh2, ncol = 2)
rownames(expCoefh2) <- names(coef(h2_hurdle_part))
colnames(expCoefh2) <- c("Count_model","Zero_hurdle_model")
expCoefh2


# stargazer(h2_hurdle)

# stargazer(h2_q)

```


- H3: Autocratic regimes with large opposition groups will be more likely to support NAGS that target democracies.\\

                + H3a: Higher likelihood of supporting at least one NAG that targets a democracy.

                + H3b: Number of NAGs that target a democracy supported will be higher. 
                
```{r echo=FALSE}

formulah3 <- NAGs_Supported ~ targ_democratic * opposition_size + WarOnTerror + ColdWar + distance_between_capitals  + W

# quasipoisson model using number of groups supported

h3_q <- glm(formula = formulah3, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h3_q)
exp(coef(h3_q))

# Hurdle model

h3_hurdle <- hurdle(formula = formulah3, data = autocracies_data)
summary(h3_hurdle)

h3_hurdle_part <- glm(I(NAGs_Supported>0) ~ targ_democratic * opposition_size + WarOnTerror + ColdWar + distance_between_capitals  + W, family  = binomial(link = "logit"), data = autocracies_data)
summary(h3_hurdle_part)
exp(coef(h3_hurdle_part))

h3_count_part <- vglm(formula = formulah3, family  = pospoisson(), data = hurdle_count_n)
summary(h3_count_part)


## Exponentiated coefficients
expCoefh3 <- exp(coef((h3_hurdle)))
expCoefh3 <- matrix(expCoefh3, ncol = 2)
rownames(expCoefh3) <- names(coef(h3_hurdle_part))
colnames(expCoefh3) <- c("Count_model","Zero_hurdle_model")
expCoefh3

# stargazer(h3_hurdle)
# stargazer(h3_q)


```



- H4: Autocratic regimes with large opposition groups will be more likely to support NAGS that target democracies by hosting training camps, all else equal. 

                + H4a: Higher likelihood of supporting at least one NAG targeting democracies by hosting training camps.

                + H4b: Number of NAGs supported by hosting training camps will be higher. 

```{r echo=FALSE}

formulah4 <- NAGS_with_Training_Camps ~ targ_democratic * opposition_size + WarOnTerror + ColdWar + distance_between_capitals  + W + NAGs_Supported

# quasipoisson model using number of groups supported

h4_q <- glm(formula = formulah4, family  = quasipoisson(link = "log"), data = autocracies_data)
summary(h4_q)
exp(coef(h4_q))

# Hurdle model

h4_hurdle <- hurdle(formula = formulah4, data = autocracies_data)
summary(h4_hurdle)

h4_hurdle_part <- glm(I(NAGS_with_Training_Camps>0) ~ targ_democratic * opposition_size + WarOnTerror + ColdWar + distance_between_capitals  + W + NAGs_Supported, family  = binomial(link = "logit"), data = autocracies_data)
summary(h4_hurdle_part)
exp(coef(h4_hurdle_part))


h4_count_part <- vglm(formula = formulah4, family  = pospoisson(), data = hurdle_count_t)
summary(h4_count_part)


cat("\n h2_hurdle - number with training camps \n")

## Exponentiated coefficients
expCoefh4 <- round(exp(coef((h4_hurdle))), digits = 5)
expCoefh4 <- matrix(expCoefh4, ncol = 2)
rownames(expCoefh4) <- names(coef(h4_hurdle_part))
colnames(expCoefh4) <- c("Count_model","Zero_hurdle_model")
expCoefh4

# stargazer(h4_q)
# stargazer(h4_hurdle)




```

## Tables

```{r echo=FALSE}

stargazer(h1_q,h1_hurdle_part, type = "text")
expCoefh1

stargazer(h2_q,h2_hurdle_part, type = "text")
expCoefh2

stargazer(h3_q,h3_hurdle_part, type = "text")
expCoefh3

stargazer(h4_q,h4_hurdle_part, type = "text")
expCoefh4
```


## Model plots

```{r echo=FALSE}

clog <- function(x) log(x + 0.5)

cfac <- function(x, breaks = NULL) {
+ if(is.null(breaks)) breaks <- unique(quantile(x, 0:10/10))
+ x <- cut(x, breaks, include.lowest = TRUE, right = FALSE)
+ levels(x) <- paste(breaks[-length(breaks)], ifelse(diff(breaks) > 1,
+ c(paste("-", breaks[-c(1, length(breaks))] - 1, sep = ""), "+"), "")) + return(x)}

```


```{r echo=FALSE}


library(ggplot2)

ggplot(autocracies_data, aes(opposition_size,NAGs_Supported)) +
        geom_count() +
        geom_smooth()

ggplot(autocracies_data, aes(opposition_size,NAGS_with_Training_Camps)) +
        geom_count() +
        geom_smooth()

library(sjPlot)
library(sjlabelled)
library(sjmisc)
theme_set(theme_sjplot())



plot_model(h1_q, title = "H1: Count of groups supported")

plot_model(h1_hurdle_part, title = "H1: Hurdle model \n Likelihood of greater than 1 group supported")



plot_model(h2_q, title = "H2: Count of groups with training camps hosted")

plot_model(h2_hurdle_part, title = "H2: Hurdle model \n Likelihood of greater than 1 group with training camp hosted")



plot_model(h3_q, title = "H3: Count of groups supported")

plot_model(h3_hurdle_part, title = "H3: Hurdle model \n Likelihood of greater than 1 group supported")



plot_model(h4_q, title = "H4: Count of groups with training camps hosted")

plot_model(h4_hurdle_part, title = "H4: Hurdle model \n Likelihood of greater than 1 group with training camp hosted")




plot_model(h1_count_part, title = "H1: Hurdle model \n Truncated Poisson Count Above Hurdle")
plot_model(h2_count_part, title = "H2: Hurdle model \n Truncated Poisson Count Above Hurdle")
plot_model(h3_count_part, title = "H3: Hurdle model \n Truncated Poisson Count Above Hurdle")
plot_model(h4_count_part, title = "H4: Hurdle model \n Truncated Poisson Count Above Hurdle")

```

## Tables for LaTeX

```{r echo=FALSE}

stargazer(h1_q,h1_hurdle_part)
expCoefh1

stargazer(h2_q,h2_hurdle_part)
expCoefh2

stargazer(h3_q,h3_hurdle_part)
expCoefh3

stargazer(h4_q,h4_hurdle_part)
expCoefh4

stargazer(h1_q,h2_q,h3_q,h4_q)

stargazer(h1_hurdle_part,h2_hurdle_part,h3_hurdle_part,h4_hurdle_part)


```

## Additional checks