---
title: "Support for non-state armed groups as domestic signaling to opposition groups"
author: "Tom Hanna"
format:
        html:
                self-contained: true
                code-fold: true
                code-summary: "Show the code"
                theme: vapor
---

## Data

This work includes data for all nondemocracies, defined as a Regimes of the World with ambiguous cases (v2x_regime_amb) < 4, Electoral autocracies and below^[Coppedge, Michael, John Gerring, Carl Henrik Knutsen, Staffan I. Lindberg, Jan Teorell, Nazifa Alizada, David Altman, Michael Bernhard, Agnes Cornell, M. Steven Fish, Lisa Gastaldi, Haakon Gjerløw, Adam Glynn, Sandra Grahn, Allen Hicken, Garry Hindle, Nina Ilchenko, Katrin Kinzelbach, Joshua Krusell, Kyle L. Marquardt, Kelly McMann, Valeriya Mechkova, Juraj Medzihorsky, Pamela Paxton, Daniel Pemstein, Josefine Pernes, Oskar Ryden, Johannes von Romer, Brigitte Seim, Rachel Sigman, Svend-Erik Skaaning, Jeffrey Staton, Aksel Sundstrom, Eitan Tzelgov, Yi-ting Wang, Tore Wig, Steven Wilson and Daniel Ziblatt. 2022. "V-Dem [Country-Year/Country-Date] Dataset v12" Varieties of Democracy (V-Dem) Project. https://doi.org/10.23696/vdemds22]. 

## Data Load

```{r warning=FALSE, message=FALSE}
options(scipen = 999)
# library(stargazer)
library(here)
library(glmx)
library(ggplot2)
library(sjPlot)

autocracies_data <- read.csv(here("data","autocracies_data_v.csv"))
```

### Name independent and control variables


```{r warning=FALSE, message=FALSE}

## Independent variable

# Opposition Size 
autocracies_data$Opposition_Size <- autocracies_data$oppsize_norm

# Strength of Democratizing Civil Society Movement
autocracies_data$Democratizing_Civil_Society_Movement <- autocracies_data$v2csanmvch_4


## Control Variables

# Minimal Winning Coalition (Selectorate measure)
# normalized measure of W based on Smith and Bueno de Mesquita 2022
autocracies_data$Minimal_Winning_Coalition <- autocracies_data$W_norm

# Distance between supporter and target capitals
autocracies_data$Distance_Between_Capitals <- autocracies_data$capdist

# Supporter CINC
autocracies_data$Supporter_CINC <- autocracies_data$supporter_cinc

# Target CINC
autocracies_data$Target_CINC <- autocracies_data$target_cinc

# Supporter State Capacity
autocracies_data$Supporter_State_Capacity <- autocracies_data$capacity

# Cold War
autocracies_data$Cold_War <- autocracies_data$ColdWar

# War on Terror
autocracies_data$War_on_Terror <- autocracies_data$WarOnTerror

# Oil income
autocracies_data$Supporter_Oil_Income <- autocracies_data$e_total_oil_income_pc

# Religious Regime Ideology
autocracies_data$Religious_Regime_Ideology <- autocracies_data$v2exl_legitideolcr_4 


```


### Measures of support: Dependent Variables

```{r warning=FALSE, message=FALSE}

# Number of NAGs supported
autocracies_data$NAGs_Supported <- autocracies_data$NumNAG_S

# Number of NAGs with training camps
autocracies_data$NAGS_with_Training_Camps <- autocracies_data$Num_S_TrainCamp


# Does the state support at least one NAG targeting another state?
autocracies_data$At_Least_1_NAG_Supported <- ifelse(autocracies_data$NAGs_Supported > 0,1,0)

# Does the state provide Other support to at least one NAG targeting another state?
autocracies_data$At_Least_1_Other_Support <- ifelse(autocracies_data$Num_S_Other > 0,1,0)

# Does the state provide Transport support to at least one NAG targeting another state?
autocracies_data$At_Least_1_Transport_Support <- ifelse(autocracies_data$Num_S_Transport > 0,1,0)

# Does the state provide Training support to at least one NAG targeting another state?
autocracies_data$At_Least_1_Training_Support <- ifelse(autocracies_data$Num_S_Training > 0,1,0)

# Does the state host at least one training camp for a NAG targeting another state?
autocracies_data$At_Least_1_Training_Camp <- ifelse(autocracies_data$NAGS_with_Training_Camps>0,1,0)

# Does the state provide Training support other than hosting a training camp for at least one NAGE targeting another state?
autocracies_data$At_Least_1_Training_Support_NonDomestic <- ifelse(autocracies_data$Num_S_Training > 0 & autocracies_data$NAGS_with_Training_Camps == 0,1,0)

# Does the state provide Weapons and Logistics Support for at least one NAG targeting another state?
autocracies_data$At_Least_1_Weapons_and_Logistics_Support <- ifelse(autocracies_data$Num_S_WeaponLog > 0,1,0)


# Does the state provide Financial Assistance for at least one NAG targeting another state?
autocracies_data$At_Least_1_Financial_Support <- ifelse(autocracies_data$Num_S_FinAid > 0,1,0)

# Does the state provide troops for at least one NAG targeting another state?
autocracies_data$At_Least_1_Troop_Support <- ifelse(autocracies_data$Num_S_Troop > 0,1,0)

# Does the state host offices for propaganda or recruitment for at least one NAG targeting another state?
autocracies_data$At_Least_1_Office <- ifelse(autocracies_data$Num_S_HeadQuar > 0,1,0)

# Does the state provide a Safe Haven for Leaders for at least one NAG targeting another state?
autocracies_data$At_Least_1_Safe_Haven_Leader <- ifelse(autocracies_data$Num_S_SafeLead > 0,1,0)

# Doest the state provide a Safe Haven for Members for at least one NAG targeting another state?
autocracies_data$At_Least_1_Safe_Haven_Member <- ifelse(autocracies_data$Num_S_SafeMem > 0,1,0)

# Does the state provide a training camp for at least one NAG targeting another state and is at least one target state democratic?
autocracies_data$TC_and_Dem_Target <- ifelse((autocracies_data$Num_S_TrainCamp > 0 & autocracies_data$target_democ == 1),1,0)


# Does the state provide any support for at least one NAG targeting a democracy?
autocracies_data$At_Least_1_Democratic_Target <- 
        ifelse((autocracies_data$target_democ == 1),1,0)

# Low cost, non-domestic support types combined

autocracies_data$Low_Cost_Non_Domestic_Support <- ifelse((
        autocracies_data$At_Least_1_Training_Support_NonDomestic == 1 | autocracies_data$At_Least_1_Other_Support == 1 | autocracies_data$At_Least_1_Transport_Support == 1),1,0)


# High cost, non-domestic support types combined

autocracies_data$High_Cost_Non_Domestic_Support <- ifelse((
        autocracies_data$At_Least_1_Troop_Support == 1 | autocracies_data$At_Least_1_Financial_Support == 1 | autocracies_data$At_Least_1_Weapons_and_Logistics_Support == 1),1,0)

# Low cost, domestic support types combined

autocracies_data$Low_Cost_Domestic_Support <- ifelse((autocracies_data$At_Least_1_Office == 1 | autocracies_data$At_Least_1_Safe_Haven_Leader == 1),1,0)

# High cost, domestic support types combined

autocracies_data$High_Cost_Domestic_Support <- ifelse((autocracies_data$At_Least_1_Safe_Haven_Member == 1 | autocracies_data$At_Least_1_Training_Camp),1,0)

# Domestic support types combined

autocracies_data$Domestic_Support <- ifelse((autocracies_data$Low_Cost_Domestic_Support == 1 | autocracies_data$High_Cost_Domestic_Support == 1),1,0)

## Non_Domestic support types combined

autocracies_data$Non_Domestic_Support <- ifelse((autocracies_data$Low_Cost_Non_Domestic_Support == 1 | autocracies_data$High_Cost_Non_Domestic_Support == 1),1,0)

# Does the state provide only low cost, non-domestic support for NAGS?

autocracies_data$Type_1_Support <- ifelse((autocracies_data$Low_Cost_Non_Domestic_Support == 1 & autocracies_data$High_Cost_Non_Domestic_Support == 0 & autocracies_data$Low_Cost_Domestic_Support == 0 & autocracies_data$High_Cost_Domestic_Support == 0),1,0)

# Does the state provide only low cost, domestic support for NAGS?

autocracies_data$Type_2_Support <- ifelse((autocracies_data$Low_Cost_Non_Domestic_Support == 0 & autocracies_data$High_Cost_Non_Domestic_Support == 0 & autocracies_data$Low_Cost_Domestic_Support == 1 & autocracies_data$High_Cost_Domestic_Support == 0),1,0)

# Does the state provide only low cost support?

autocracies_data$Type_3_Support <- ifelse((autocracies_data$At_Least_1_NAG_Supported == 1 & autocracies_data$High_Cost_Non_Domestic_Support == 0 & autocracies_data$High_Cost_Domestic_Support == 0),1,0)

# Does the state provide only Non Domestic support?

autocracies_data$Type_4_Support <- ifelse((autocracies_data$At_Least_1_NAG_Supported == 1 & autocracies_data$Low_Cost_Domestic_Support == 0 & autocracies_data$High_Cost_Domestic_Support == 0),1,0)

# Does the state provide only Low cost or Non Domestic support?

autocracies_data$Type_5_Support <- ifelse((autocracies_data$At_Least_1_NAG_Supported == 1 & autocracies_data$High_Cost_Domestic_Support == 0),1,0)

# Does the state provide only support other than training camps or Troops)?
autocracies_data$Type_6_Support <- ifelse((autocracies_data$At_Least_1_NAG_Supported == 1 & autocracies_data$At_Least_1_Training_Camp == 0 & autocracies_data$At_Least_1_Troop_Support == 0),1,0)

# Support only other than training camps?
autocracies_data$Type_7_Support <- ifelse((autocracies_data$At_Least_1_NAG_Supported == 1 & autocracies_data$At_Least_1_Training_Camp == 0),1,0)

# High visibility with democratic target

autocracies_data$High_Visibility_Democratic_Target <- ifelse((autocracies_data$target_democ == 1 & autocracies_data$Domestic_Support == 1),1,0)

```

### Summary Statistics: Dependent Variables

```{r}

# Does the state support at least one NAG targeting another state?  
cat("At least one NAG supported:", sum(autocracies_data$At_Least_1_NAG_Supported), "\n","No NAGs supported:", sum(autocracies_data$At_Least_1_NAG_Supported == 0), "\n")

# Number of NAGs supported

cat("Number of NAGs support:", sum(autocracies_data$NAGs_Supported), "\n")


# Number of NAGs with training camps



# Does the state provide Other support to at least one NAG targeting another state?
cat("At least one NAG supported with Other type support:", sum(autocracies_data$At_Least_1_Other_Support), "\n","No NAGs supported:", sum(autocracies_data$At_Least_1_Other_Support == 0), "\n")


# Does the state provide Transport support to at least one NAG targeting another state?
cat("At least one NAG supported with Transportation:", sum(autocracies_data$At_Least_1_Transport_Support), "\n","No NAGs supported:", sum(autocracies_data$At_Least_1_Transport_Support == 0), "\n")

# Does the state provide Training support to at least one NAG targeting another state?
cat("At least one NAG supported with Training:", sum(autocracies_data$At_Least_1_Training_Support), "\n","No NAGs supported:", sum(autocracies_data$At_Least_1_Training_Support == 0), "\n")       

# Does the state host at least one training camp for a NAG targeting another state?
cat("At least one NAG supported with Training Camp:", sum(autocracies_data$At_Least_1_Training_Camp), "\n","No NAGs supported:", sum(autocracies_data$At_Least_1_Training_Camp == 0), "\n")

# Does the state provide Training support other than hosting a training camp for at least one NAG targeting another state?

cat("At least one NAG with Non-Domestic Training support:", sum(autocracies_data$At_Least_1_Training_Support_NonDomestic), "\n","No NAGs supported:", sum(autocracies_data$At_Least_1_Training_Support_NonDomestic == 0), "\n")


# Does the state provide Weapons and Logistics Support for at least one NAG targeting another state?

cat("At least one NAG with Weapons and Logistics support:", sum(autocracies_data$At_Least_1_Weapons_and_Logistics_Support), "\n","No NAGs supported:", sum(autocracies_data$At_Least_1_Weapons_and_Logistics_Support == 0), "\n")

# Does the state provide Financial Assistance for at least one NAG targeting another state?

cat("At least one NAG with Financial Assistance:", sum(autocracies_data$At_Least_1_Financial_Support), "\n","No NAGs supported:", sum(autocracies_data$At_Least_1_Financial_Support == 0), "\n")

# Does the state provide troops for at least one NAG targeting another state?

cat("At least one NAG with Troop Support:", sum(autocracies_data$At_Least_1_Troop_Support), "\n","No NAGs supported:", sum(autocracies_data$At_Least_1_Troop_Support == 0), "\n")

# Does the state host offices for propaganda or recruitment for at least one NAG targeting another state?

cat("At least one NAG with domestic Office:", sum(autocracies_data$At_Least_1_Office), "\n","No NAGs supported:", sum(autocracies_data$At_Least_1_Office == 0), "\n")

# Does the state provide a Safe Haven for Leaders for at least one NAG targeting another state?

cat("At least one NAG with domestic Safe Haven for Leader(s):", sum(autocracies_data$At_Least_1_Safe_Haven_Leader), "\n","No NAGs supported:", sum(autocracies_data$At_Least_1_Safe_Haven_Leader == 0), "\n")

# Doest the state provide a Safe Haven for Members for at least one NAG targeting another state?

cat("At least one NAG with domestic Safe Haven for Members:", sum(autocracies_data$At_Least_1_Safe_Haven_Member), "\n","No NAGs supported:", sum(autocracies_data$At_Least_1_Safe_Haven_Member == 0), "\n")


# Does the state provide a training camp for at least one NAG targeting another state and is at least one target state democratic?

cat("At least one NAG with domestic Training Camp and \n at least one target state is democratic:", sum(autocracies_data$TC_and_Dem_Target, na.rm = TRUE), "\n","No NAGs supported:", sum(autocracies_data$TC_and_Dem_Target  == 0, na.rm = TRUE), "\n")

summary(autocracies_data$TC_and_Dem_Target )

# Does the state provide any support for at least one NAG targeting a democracy?

cat("At least \n one target state is democratic:", sum(autocracies_data$At_Least_1_Democratic_Target, na.rm = TRUE), "\n","No NAGs supported:", sum(autocracies_data$At_Least_1_Democratic_Target == 0, na.rm = TRUE), "\n")

summary(autocracies_data$At_Least_1_Democratic_Target)



# Low cost, non-domestic support types combined

cat("Low cost, non-domestic support types combined:", sum(autocracies_data$Low_Cost_Non_Domestic_Support), "\n")

# High cost, non-domestic support types combined

cat("High cost, non-domestic support types combined:", sum(autocracies_data$High_Cost_Non_Domestic_Support), "\n")

# Low cost, domestic support types combined

cat("Low cost, domestic support types combined:", sum(autocracies_data$Low_Cost_Domestic_Support), "\n")

# High cost, domestic support types combined

cat("High cost, domestic support types combined:", sum(autocracies_data$High_Cost_Domestic_Support), "\n")

# Domestic support types combined

cat("Domestic support types combined:", sum(autocracies_data$Domestic_Support), "\n")



# Does the state provide only low cost, non-domestic support for NAGS?

cat("Only low cost, non-domestic support:", sum(autocracies_data$Type_1_Support), "\n")

# Does the state provide only low cost, domestic support for NAGS?

cat("Only low cost, domestic support:", sum(autocracies_data$Type_2_Support), "\n")

# Does the state provide only low cost support?

cat("Only low cost support:", sum(autocracies_data$Type_3_Support), "\n")


# Does the state provide only Non Domestic support?

cat("Only Non Domestic support:", sum(autocracies_data$Type_4_Support), "\n")

# Does the state provide only Low cost or Non Domestic support?

cat("Only Low cost or Non Domestic support:", sum(autocracies_data$Type_5_Support), "\n")


# Does the state provide only Low and medium cost support (no training camps, no troop support)?


cat("Only Low and medium cost support \n No training camps or troops:", sum(autocracies_data$Type_6_Support), "\n")

# Support only other than training camps?

cat("Only support other than training camps:", sum(autocracies_data$Type_7_Support), "\n")

# High visibility with democratic target

cat("High visibility with democratic target:", sum(autocracies_data$High_Visibility_Democratic_Target, na.rm = TRUE), "\n")

```


### Dependent Variable Plots

```{r}

plot_df <- autocracies_data


# High cost, domestic support types combined

plot_df$High_Cost_Domestic_Support <- as.factor(plot_df$High_Cost_Domestic_Support)

barplot(table(plot_df$High_Cost_Domestic_Support), main = "High Cost Domestic Support", xlab = "Number of States", ylab = "Number of NAGs")

# Low cost, domestic support types combined

plot_df$Low_Cost_Domestic_Support <- as.factor(plot_df$Low_Cost_Domestic_Support)            

barplot(table(plot_df$Low_Cost_Domestic_Support), main = "Low Cost Domestic Support", xlab = "Number of States", ylab = "Number of NAGs")

# High cost, non-domestic support types combined

plot_df$High_Cost_Non_Domestic_Support <- as.factor(plot_df$High_Cost_Non_Domestic_Support)

barplot(table(plot_df$High_Cost_Non_Domestic_Support), main = "High Cost Non Domestic Support", xlab = "Number of States", ylab = "Number of NAGs")

# Low cost, non-domestic support types combined

plot_df$Low_Cost_Non_Domestic_Support <- as.factor(plot_df$Low_Cost_Non_Domestic_Support)

barplot(table(plot_df$Low_Cost_Non_Domestic_Support), main = "Low Cost Non Domestic Support", xlab = "Number of States", ylab = "Number of NAGs")

# Domestic support types combined

plot_df$Domestic_Support <- as.factor(plot_df$Domestic_Support)

barplot(table(plot_df$Domestic_Support), main = "Domestic Support", xlab = "Number of States", ylab = "Number of NAGs")

# Does the state provide only low cost, non-domestic support for NAGS?

plot_df$Type_1_Support <- as.factor(plot_df$Type_1_Support)

barplot(table(plot_df$Type_1_Support), main = "Only low cost, non-domestic support", xlab = "Number of States", ylab = "Number of NAGs")

# Does the state provide only low cost, domestic support for NAGS?

plot_df$Type_2_Support <- as.factor(plot_df$Type_2_Support)

barplot(table(plot_df$Type_2_Support), main = "Only low cost, domestic support", xlab = "Number of States", ylab = "Number of NAGs")

# Does the state provide only low cost support?

plot_df$Type_3_Support <- as.factor(plot_df$Type_3_Support)

barplot(table(plot_df$Type_3_Support), main = "Only low cost support", xlab = "Number of States", ylab = "Number of NAGs")

# Does the state provide only Non Domestic support?

plot_df$Type_4_Support <- as.factor(plot_df$Type_4_Support)

barplot(table(plot_df$Type_4_Support), main = "Only Non Domestic support", xlab = "Number of States", ylab = "Number of NAGs")

# Does the state provide only Low cost or Non Domestic support?

plot_df$Type_5_Support <- as.factor(plot_df$Type_5_Support)

barplot(table(plot_df$Type_5_Support), main = "Only Low cost or Non Domestic support", xlab = "Number of States", ylab = "Number of NAGs")

# Does the state provide only Low and medium cost support (no training camps, no troop support)?

plot_df$Type_6_Support <- as.factor(plot_df$Type_6_Support)

barplot(table(plot_df$Type_6_Support), main = "Only Low and medium cost support \n No training camps or troops", xlab = "Number of States", ylab = "Number of NAGs")

# Support only other than training camps?

plot_df$Type_7_Support <- as.factor(plot_df$Type_7_Support)

barplot(table(plot_df$Type_7_Support), main = "Only support other than training camps", xlab = "Number of States", ylab = "Number of NAGs")

# Democratic target

plot_df$Democratic_Target <- as.factor(plot_df$At_Least_1_Democratic_Target)

barplot(table(plot_df$Democratic_Target), main = "Democratic target", xlab = "Number of States", ylab = "Number of NAGs")


# High visibility with democratic target

plot_df$High_Visibility_Democratic_Target <- as.factor(plot_df$High_Visibility_Democratic_Target)

barplot(table(plot_df$High_Visibility_Democratic_Target), main = "High visibility (Domestic) with democratic target", xlab = "Number of States", ylab = "Number of NAGs")

# Democratic Target with Training Camp

plot_df$Democratic_Target_Training_Camp <- as.factor(plot_df$TC_and_Dem_Target)

barplot(table(plot_df$Democratic_Target_Training_Camp), main = "Democratic Target with Training Camp", xlab = "Number of States", ylab = "Number of NAGs")

```


## Hypotheses

### Hypothesis H1

*H1: States with higher levels of domestic opposition will be more likely to provide high cost, high visibility support for NAGs than states with lower levels of domestic oppositoin, all else equal.*



```{r}
# logit model with base control variables - Cold War, War on Terror, Capitals Distance, W, and State Capacity
model_h1 <- glm(High_Cost_Domestic_Support ~ Opposition_Size + Minimal_Winning_Coalition + Distance_Between_Capitals + Supporter_State_Capacity + Cold_War + War_on_Terror, data = autocracies_data, family = binomial(link = "logit"))
summary(model_h1)

# probit model with base control variables - Cold War, War on Terror, Capitals Distance, W, and State Capacity
model_h1_probit <- glm(High_Cost_Domestic_Support ~ Opposition_Size + Minimal_Winning_Coalition + Distance_Between_Capitals + Supporter_State_Capacity + Cold_War + War_on_Terror, data = autocracies_data, family = binomial(link = "probit"))
summary(model_h1_probit)




#logit model with full controls - base controls plus supporter oil income, religious regime ideology, 

model_h1_full <- glm(High_Cost_Domestic_Support ~ Opposition_Size + Minimal_Winning_Coalition + Distance_Between_Capitals + Supporter_State_Capacity + Cold_War + War_on_Terror + Supporter_Oil_Income + Religious_Regime_Ideology, data = autocracies_data, family = binomial(link = "logit"))

summary(model_h1_full)


```



### Hypothesis H2

*H2: Low cost, low domestic visibility support for NAGs will have no significant relationship with opposition size, all else equal.*


```{r}
# logit model with base control variables - Cold War, War on Terror, Capitals Distance, W, and State Capacity
model_h2 <- glm(Low_Cost_Non_Domestic_Support ~ Opposition_Size + Minimal_Winning_Coalition + Distance_Between_Capitals + Supporter_State_Capacity + Cold_War + War_on_Terror, data = autocracies_data, family = binomial(link = "logit"))
summary(model_h2)

# logit model with full control variables - base controls plus supporter oil income, religious regime ideology

model_h2_full <- glm(Low_Cost_Non_Domestic_Support ~ Opposition_Size + Minimal_Winning_Coalition + Distance_Between_Capitals + Supporter_State_Capacity + Cold_War + War_on_Terror + Supporter_Oil_Income + Religious_Regime_Ideology, data = autocracies_data, family = binomial(link = "logit"))
summary(model_h2_full)


```


### Hypothesis H3

*H3: States with higher levels of domestic opposition will be more likely to provide low cost, domestic support for NAGs than states with lower levels of domestic opposition, all else equal.*

```{r}
# logit model with base control variables - Cold War, War on Terror, Capitals Distance, W, and State Capacity
model_h3 <- glm(Low_Cost_Domestic_Support ~ Opposition_Size + Minimal_Winning_Coalition + Distance_Between_Capitals + Supporter_State_Capacity + Cold_War + War_on_Terror, data = autocracies_data, family = binomial(link = "logit"))
summary(model_h3)

# logit model with full control variables - base controls plus supporter oil income, religious regime ideology

model_h3_full <- glm(Low_Cost_Domestic_Support ~ Opposition_Size + Minimal_Winning_Coalition + Distance_Between_Capitals + Supporter_State_Capacity + Cold_War + War_on_Terror + Supporter_Oil_Income + Religious_Regime_Ideology, data = autocracies_data, family = binomial(link = "logit"))
summary(model_h3_full)


```

### Hypothesis H4

*H4: States with higher levels of domestic opposition will be less likely to provide high cost, non-domestic support for NAGS, all else equal.*

```{r}

# logit model with base control variables - Cold War, War on Terror, Capitals Distance, W, and State Capacity
model_h4 <- glm(High_Cost_Non_Domestic_Support ~ Opposition_Size + Minimal_Winning_Coalition + Distance_Between_Capitals + Supporter_State_Capacity + Cold_War + War_on_Terror, data = autocracies_data, family = binomial(link = "logit"))
summary(model_h4)



```

#### Hypothesis H4a

*H4a: States with higher levels of domestic opposition will be less likely to provide financial assistance to NAGs, all else equal.*

```{r} 
# logit model with base controls - Cold War, War on Terror, Capitals Distance, W, and State Capacity
model_h4a <- glm(At_Least_1_Financial_Support ~ Opposition_Size + Minimal_Winning_Coalition + Distance_Between_Capitals + Supporter_State_Capacity + Cold_War + War_on_Terror, data = autocracies_data, family = binomial(link = "logit"))    
summary(model_h4a)

# probit model with base controls - Cold War, War on Terror, Capitals Distance, W, and State Capacity
model_h4a_probit <- glm(At_Least_1_Financial_Support ~ Opposition_Size + Minimal_Winning_Coalition + Distance_Between_Capitals + Supporter_State_Capacity + Cold_War + War_on_Terror, data = autocracies_data, family = binomial(link = "probit"))
summary(model_h4a_probit)

# logit model with full controls - base controls plus supporter oil income, religious regime ideology

model_h4a_full <- glm(At_Least_1_Financial_Support ~ Opposition_Size + Minimal_Winning_Coalition + Distance_Between_Capitals + Supporter_State_Capacity + Cold_War + War_on_Terror + Supporter_Oil_Income + Religious_Regime_Ideology, data = autocracies_data, family = binomial(link = "logit"))
summary(model_h4a_full)

```


### Hypothesis H5

The positive relationship between opposition size and support for NAGs will increase as the visibility of support increases. The relationship to cost will likely be nonlinear, with too little cost being ineffective and too much cost being too great compared to the cost of repression. 

We cam measure this with Cliff's Delta for the effect of opposition size on each dependent variable. Cliff's delta is designed for ordinal variables. In this case the binary variable support or not support is also an ordinal variable with ranks of 0 for no support and 1 for support, so the use of Cliff's Delta is appropriate.^[Torchiano, Marco. "effsize: Efficient Effect Size Computation", doi = "10.5281/zenodo.1480624", url = "https://CRAN.R-project.org/package=effsize"]

From suggestion to use Cohen's d to compare effect sizes of the same independent variable on two different continuous variables.^[https://stats.stackexchange.com/questions/333447/compare-the-relative-effects-of-an-independent-variable-on-two-different-depende]

```{r}
library(effsize)

domestic_d <- cliff.delta(autocracies_data$Opposition_Size, autocracies_data$Domestic_Support)

non_domestic_d <- cliff.delta(autocracies_data$Opposition_Size, autocracies_data$Non_Domestic_Support)

high_cost_domestic_d <- cliff.delta(autocracies_data$Opposition_Size, autocracies_data$High_Cost_Domestic_Support)


low_cost_domestic_d <- cliff.delta(autocracies_data$Opposition_Size, autocracies_data$Low_Cost_Domestic_Support)



high_cost_non_domestic_d <- cliff.delta(autocracies_data$Opposition_Size, autocracies_data$High_Cost_Non_Domestic_Support)




low_cost_not_domestic_d <- cliff.delta(autocracies_data$Opposition_Size, autocracies_data$Low_Cost_Non_Domestic_Support)

cat("Effect size for H5a: High Cost, Domestic Support", "\n")
high_cost_domestic_d

cat("Effect size for H5b: Low Cost, Domestic Support", "\n")
low_cost_domestic_d

cat("Effect size for H5c: High Cost, Non-Domestic Support", "\n")
high_cost_non_domestic_d

cat("Effect size for H5d: Low Cost, Non-Domestic Support", "\n")
low_cost_not_domestic_d
cat("\n")
cat("Note that the relationship between opposition size and support for NAGs is negative and non-significant for low cost, non-domestic support. This is the opposite of the effect for high cost, non-domestic support and as predicted for the signaling hypothesis over low cost capacity building.", "\n")


cat("Effect size for H5e: Domestic Support", "\n")

domestic_d

cat("Effect size for H5f: Non-Domestic Support", "\n")

non_domestic_d


```
While the effect sizes are not clearly separated for the four broad categories, the negative effect for low cost, low visibility support and the overall preference for high visibility over low visibility support is consistent with the signaling theory of support for NAGs. Since the purpose of signaling is to provide a signal that while costly is less costly than whatever is being signaled, it makes sense that the effect size for low cost, high visibility support is opposite the effect for low cost, low visibility support and larger than the effect for high cost, low visibility support.